---
title: "R Notebook"
output: html_notebook
---

# Find out how the risktaking was set together and how they are measured
# Find out about the overlap
- same countries 
- facid wrap --> Plot by country
- scatterplots --> mean country // mean risk 

# Concept: What do we want 
- Risktaking and age slope
- Plot it by how steep the slope is
--> Run it in an mixed effect model (see paper from Rui)

###########
Next steps: 
- what visualisation do we want to do (why)? 
- write read me --> why do we do certain steps 
- always age and gender in the plots
- Intercept age, intercept for age, intercept gender, intercept n


#Load packages 
```{r}
library(data.table)
library(tidyr)
library(haven)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(lmtest)
```


#Add data GPS
```{r}
# Einlesen des Datensets
gps_data <- haven::read_dta("/Users/laurabazzigher/Documents/GitHub/risk_wvs/data/dataset/GPS_dataset_individual_level/individual_new.dta")

# Anzeige der ersten Zeilen des Datensets
head(country_data)
```
# Number of courtries 
```{r}
# Determine the number of different countries
number_of_countries <- length(unique(gps_data$country))

# Display the number of different countries
number_of_countries
```


# Clean the data from missing values
```{r}
# Clean the data by removing records with missing values
cleaned_data <- gps_data %>%
  drop_na(country, isocode, risktaking, gender, age)

# Calculate the number of records removed per variable
records_removed_per_variable <- colSums(is.na(gps_data)) - colSums(is.na(cleaned_data))

# Display the cleaned data
cleaned_data

# Display the number of records removed per variable
records_removed_per_variable
```

# List of all variable
```{r}
# List all variables
variable_list <- names(cleaned_data) # OR colnames(your_data)

# Display the list of variables
print(variable_list)
```

# Variance of some Items
```{r}
# Calculate the variance of the "patience" variable
variance_patience <- var(cleaned_data$patience, na.rm = TRUE)
variance_risktaking <- var(cleaned_data$risktaking, na.rm = TRUE)
variance_age <- var(cleaned_data$age, na.rm = TRUE)

# Display the variance of the "patience" variable
variance_patience
variance_risktaking
variance_age
```
# Histogram of some variables
```{r}
hist(cleaned_data$age, main = "Histogram of Age", xlab = "age", ylab = "Frequency")
hist(cleaned_data$patience, main = "Histogram of patience", xlab = "patience", ylab = "Frequency")
hist(cleaned_data$risktaking, main = "Histogram of risktaking", xlab = "risktaking", ylab = "Frequency")
```
# Boxplot of some variables
```{r}
boxplot(cleaned_data$age, main = "Boxplot of Age")
boxplot(cleaned_data$patience, main = "Boxplot of Patience")
boxplot(cleaned_data$risktaking, main = "Boxplot of Risktaking")
```
# All about the age
```{r}
# Age Range
age_min <- min(cleaned_data$age, na.rm = TRUE)
age_max <- max(cleaned_data$age, na.rm = TRUE)

# Average Age
average_age <- mean(cleaned_data$age, na.rm = TRUE)

# Median Age
median_age <- median(cleaned_data$age, na.rm = TRUE)

# Display the age statistics
cat("Age Range: ", age_min, " to ", age_max, "\n")
cat("Average Age: ", average_age, "\n")
cat("Median Age: ", median_age, "\n")
```

# All about the gender
```{r}
# Calculate the counts of females (gender = 1) and males (gender = 2)
gender_counts <- table(cleaned_data$gender)

# Display the counts
cat("Number of Females: ", gender_counts[1], "\n")
cat("Number of Males: ", gender_counts[2], "\n")
```

# Table with country and gender
```{r}
# Create a table that breaks down the number of participants by country and gender
gender_by_country <- xtabs(~ country + gender, data = cleaned_data)

# Rename columns and rows for better readability
colnames(gender_by_country) <- c("Female", "Male")
rownames(gender_by_country) <- unique(cleaned_data$country)

# Display the table
gender_by_country
```
# Create a table with the following information: country, isocode, n (count of participants), female percentage (%), mean age, age range, and risktaking
####### add intercept and slope (age, gender, parental status, occupational status, education)
```{r}
# Group the data by country
table_data <- gps_data %>%
  group_by(country, isocode) %>%
  summarize(
    n = n(),
    female_percentage = mean(gender == 1) * 100,
    mean_age = mean(age, na.rm = TRUE),
    age_range = paste(min(age, na.rm = TRUE), "-", max(age, na.rm = TRUE)),
    mean_risktaking = mean(risktaking, na.rm = TRUE)
  )

# Display the table
table_data
```

# Create a new column "age_group" with the age categories
```{r}
cleaned_data$agecat <- cut(
  cleaned_data$age,
  breaks = c(15, 20, 30, 40, 50, 60, 70, 80, Inf), # The category boundaries
  labels = c("15-19", "20-29", "30-39", "40-49", "50-59", "60-69", "70-79", "80+"), # The category labels
  right = FALSE # Left end (inclusive), right end (exclusive)
)

# Display the new column
head(cleaned_data)
```

# Number of participants in each age category
```{r}
# number of participants in each age category
agecat_counts <- table(cleaned_data$agecat)

# Display the number of participants in the age categories
print(agecat_counts)
```


# Perform a correlation analysis on variables patience, risktaking, altruism and trust
```{r}
# Calculate the correlation matrix with NA removal
correlation_matrix <- cor(cleaned_data[, c("patience", "risktaking", "altruism", "trust")], use = "pairwise.complete.obs")

# Print the correlation matrix
print(correlation_matrix)

```

#############################################
# checking the assumptions in a linear regression  
```{r}
# Scatterplot to check for linearity
ggplot(cleaned_data, aes(x = age, y = risktaking)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "blue") +
  labs(title = "Scatterplot for Linearity Check")
```
```{r}
# Residual vs. Fitted plot to check for homoskedasticity
model <- lm(risktaking ~ age, data = cleaned_data)
ggplot() +
  geom_point(aes(x = fitted(model), y = residuals(model))) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  labs(title = "Residuals vs. Fitted Values for Homoskedasticity Check")
```

```{r}
# Q-Q plot to check for normality of residuals
qqnorm(residuals(model))
qqline(residuals(model))
```

```{r}
# Correlation matrix to check for multicollinearity
cor(cleaned_data[c("age", "risktaking")])
```

```{r}
# Durbin-Watson test for autocorrelation
dwtest(model)
```

```{r}
# Residual vs. Leverage plot to check for outliers
ggplot() +
  geom_point(aes(x = hatvalues(model), y = residuals(model))) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  labs(title = "Residuals vs. Leverage for Outlier Check")
```

#############################################



#Preparing for linear regression
```{r}
# Check for missing values in 'Country' and 'Risktaking' columns
missing_country <- anyNA(cleaned_data$country)
missing_risktaking <- anyNA(cleaned_data$risktaking)

# Print the results
cat("Missing values in 'Country': ", missing_country, "\n")
cat("Missing values in 'Risktaking': ", missing_risktaking, "\n")

```


```{r}
# Clean the data by removing records with missing values
cleaned_data <- gps_data %>%
  drop_na(country, risktaking, age)

# Split the data by country and perform linear regression for each country
regression_results <- cleaned_data %>%
  group_by(country) %>%
  do(model = lm(risktaking ~ age, data = .)) %>%
  summarize(
    country = first(country),
    intercept = summary(model)$coefficients[1],
    slope = summary(model)$coefficients[2],
    r_squared = summary(model)$r.squared
  )

# Display regression results for each country
print(regression_results)
```


# analyze the results by using "Balkendiagramm
###### what does 0 mean? // centered age = mean age of the sample
```{r}
ggplot(data = regression_results, aes(x = country, y = intercept)) +
  geom_bar(stat = "identity", fill = "blue") +
  labs(title = "Intercepts for Risktaking by Country", x = "Country", y = "Intercept Value") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
# View the countries with intercept values over 0.75
```{r}
high_intercept_countries <- subset(regression_results, intercept > 0.75)

# View the countries with intercept values over 0.75
print(high_intercept_countries)
```


# Scatterplots for 'high_intercept_countries' contains the top 17 countries
```{r}
# Create scatterplots with regression lines for countries with intercept > 0.75 and smaller points
plots <- lapply(1:nrow(regression_results), function(i) {
  country <- regression_results$country[i]
  intercept <- regression_results$intercept[i]
  
  if (intercept > 0.75) {
    p <- ggplot(subset(cleaned_data, country == country), aes(x = age, y = risktaking)) +
      geom_point(size = 0.5) +  # Set the size to a smaller value (e.g., 2)
      geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = "blue") +
      labs(title = paste("Linear Regression for", country),
           subtitle = paste("Intercept:", round(intercept, 2)))
    print(p)
  }
})

# Save the plots in a directory
dir.create("individual_country_plots", showWarnings = FALSE)
setwd("individual_country_plots")

for (i in seq_along(plots)) {
  filename <- paste0("plot_", i, ".png")
  ggsave(filename, plot = plots[[i]], width = 8, height = 6)
}

# Switch back to the original working directory
setwd("..")

print("Individual plots for countries with intercept > 0.75 and smaller points are saved in the 'individual_country_plots' directory.")
```

# Create scatterplots with regression lines for individual countries
```{r}
# Examples for countries
regression_results <- data.frame(
  country = c("Algeria", "Argentina", "Austria"),
  intercept = c(0.92053422, 0.51698822, 0.42606684),
  slope = c(-0.0146641801, -0.0115569623, -0.0108763042),
  r_squared = c(5.232529e-02, 5.638271e-02, 3.539810e-02	)
)

# Create scatterplots with regression lines for each country
plots <- lapply(seq_len(nrow(regression_results)), function(i) {
  country <- regression_results$country[i]
  intercept <- regression_results$intercept[i]
  slope <- regression_results$slope[i]
  r_squared <- regression_results$r_squared[i]
  
  p <- ggplot(subset(cleaned_data, country == country), aes(x = age, y = risktaking)) +
    geom_point() +
    geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = "blue") +
    labs(title = paste("Linear Regression for", country),
         subtitle = paste("Intercept:", round(intercept, 2),
                           "Slope:", round(slope, 2),
                           "R-squared:", round(r_squared, 2)))
  print(p)
})

# Save the plots in a directory
dir.create("individual_country_plots", showWarnings = FALSE)
setwd("individual_country_plots")

for (i in seq_along(plots)) {
  filename <- paste0("plot_", i, ".png")
  ggsave(filename, plot = plots[[i]], width = 8, height = 6)
}

# Switch back to the original working directory
setwd("..")

print("Individual plots are saved in the 'individual_country_plots' directory.")
```

# Create a scatterplot with separate regression lines for each country
```{r}
ggplot(cleaned_data, aes(x = age, y = risktaking, color = country)) +
  geom_point(size = 0.2) +                           # Adjust point size
  geom_smooth(method = "lm", se = FALSE, size = 0.5, linetype = "solid") + # Adjust line size and type
  labs(title = "Scatterplot with Regression Lines for risktaking and age by Country", 
       x = "Age", y = "Risktaking") +
  theme(legend.position = "bottom",              # Move the legend below the graph
        legend.key.size = unit(0.1, "in"))      # Adjust the size of the legend key
```

# Scatterplot with include both individual country regression lines and an overall regression line
```{r}
# Calculate the overall regression line
overall_lm <- lm(risktaking ~ age, data = cleaned_data)

# Create a scatterplot with separate regression lines for each country
# and an overall regression line
ggplot(cleaned_data, aes(x = age, y = risktaking, color = country)) +
  geom_point(size = 0.5) +                      # Adjust point size
  geom_smooth(method = "lm", se = FALSE, size = 0.5) + # Solid line for individual countries
  geom_abline(intercept = coef(overall_lm)[1], slope = coef(overall_lm)[2], 
              color = "red", size = 1) + # Add the overall regression line in red
  labs(title = "Scatterplot with Regression Lines for risktaking and age by Country", 
       x = "Age", y = "Risktaking") +
  theme(legend.position = "bottom",          # Move the legend below the graph
        legend.key.size = unit(0.1, "in"))  # Adjust the size of the legend key
```


