---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

```{r}
rm(list = ls())
```

##### We first prepare World Values Survey (WVS) data 
##### We (e.g., exclude cases that have missing information on key variables, such as age, sex, 
##### education, etc.; dichotomize variables; transform risk taking item)
```{r}
dateipfad <- "\\\\kt.ktzh.ch\\Personal\\Home01\\B117T23\\Documents\\Laura Bazzigher\\Privat\\Studium\\Riskktaking\\Data"

data_wv5 <- readRDS(file.path(dateipfad, "F00007944-WV5_Data_R_v20180912.rds"))

load(file.path(dateipfad, "WV6_Data_R_v20201117.rdata"))
head(data_wv5)
head(WV6_Data_R_v20201117)
```
# read in a file with the country names and respective numeric codes used in WVS
```{r}
countrynames <- read.csv(file.path(dateipfad, "countrynames.txt"), header = FALSE, as.is = TRUE) 
```

# select a subset of the WVS data (Wave 5), including wave, country, 10 Schwartz items (including the risk item), and demographics
```{r} 
data5 <- data_wv5[, c("V1", "V2", "V80","V81","V82","V83","V84","V85","V86","V87","V88","V89", "V235", "V237", "V238", "V241", "V55", "V56", "V260")]
names(data5) <- c("wave", "country","creativity","money","security","goodtime","help","success","risk","proper","environment","tradition", "sex", "age", "education", "employed", "married", "children", "year")
head(data5)
```


# DATA CHECK: comparing the N from data5 against the counts from counts provided in www.worldvaluessurvey.org
```{r}
data5[,"country_lab"]=NA
countries=unique(data5$country)
for(row in 1:length(countries))
{
  data5[data5$country==countries[row],"country_lab"]=countrynames[countrynames[,1]==countries[row],2]
}
table(data5$country_lab)
```

# select a subset of the WVS data (Wave 6), including wave, country, 10 Schwartz items (including the risk item), and demographics 
```{r}
data6 = WV6_Data_R_v20201117[, c("V1", "V2","V70","V71","V72","V73","V74B","V75","V76","V77","V78","V79", "V240", "V242", "V248", "V229", "V57", "V58", "V262")]
names(data6) = c("wave", "country","creativity","money","security","goodtime","help","success","risk","proper","environment","tradition", "sex", "age", "education", "employed", "married", "children", "year")

head(data6)
```

```{r}
data6[,"country_lab"]=NA
countries=unique(data6$country)
for(row in 1:length(countries))
{
  data6[data6$country==countries[row],"country_lab"]=countrynames[countrynames[,1]==countries[row],2] 
}
table(data6$country_lab)
```


# Data looks ok so we bind the two waves...
```{r}
data = rbind(data5, data6)
head(data)
```
# Laura: Check Country and Country-nr
```{r}
# Eindeutige Kombinationen von country_lab und country aus data
unique_countries <- unique(data[, c("country_lab", "country")])
unique_countries
```


# PARTICIPANT EXCLUSION 
#### We exclude individuals for which we do not know sex, age, education, employment status, marital status, or number of children
```{r}
data = subset(data, risk > 0 & sex > 0 & age >0 & education > 0 & employed > 0 & married > 0 & children >= 0)

length(unique(data$country)) # number of countries
nrow(data) # number of individuals
range(data$age) # age
table(data$sex) # sex table(data$sex)/nrow(data)
```

# create a categorical age variable (for example, to plot response frequencies by category)
```{r}
data$agecat[data$age<20]="15-19"
data$agecat[data$age>=20 & data$age <30] = "20-29"
data$agecat[data$age>=30 & data$age <40] = "30-39"
data$agecat[data$age>=40 & data$age <50] = "40-49"
data$agecat[data$age>=50 & data$age <60] = "50-59"
data$agecat[data$age>=60 & data$age <70] = "60-69"
data$agecat[data$age>=70 & data$age <80] = "70-79"
data$agecat[data$age>=80] = "80+"

table(data$age)
table(data$agecat)
```
#EDUCATION
#1 No formal education
#2 Incomplete primary school
#3 Complete primary school
#4 Incomplete secondary school: technical/vocational type
#5 Complete secondary school: technical/vocational type
#6 Incomplete secondary: university-preparatory type
#7 Complete secondary: university-preparatory type
#8 Some university-level education, without degree
#9 University-level education, with degree


# create a categorical education variable (with fewer categories than the original)
```{r}
attach(data)
data$education_cat[education < 3] = "incomplete or no primary education"
data$education_cat[education > 2 & education <= 6] <- "no uni"
data$education_cat[education >= 7] <- "uni"
detach(data)
table(data$education)
```
#EMPLOYED
#Yes, has paid employment:
#Full time employee (30 hours a week or more) 1 
#Part time employee (less than 30 hours a week) 2 
#Self employed 3
#No, no paid employment:
#Retired/pensioned 4 
#Housewife not otherwise employed 5
#Student 6 
#Unemployed 7
#Other (write in): 8


# Dichotomizing Variables: This helps estimating and interpreting the models later on...
```{r}
data$sex = ifelse(data$sex == 1, 0, 1) # sex: male vs. female
data$children = ifelse(data$children == 0, 0, 1) # children: no vs. yes
data$married = ifelse(data$married == 1, 1, 0) # married: yes vs. no
data$employed = ifelse(data$employed < 4, 1, 0) # employed: yes vs. no
data$education = ifelse(data$education < 4, 0, 1) # education: no primary vs. primary+ 
```

# Read in country names, assign country labels to WVS data, and add the hardship indicators + hardship index 
#### (see below for more analyses on the hardship index)

# read in file that contains hardship indicators manually collected from CIA factbook, WHO, and World Bank 
#### (see Supplemental Materials for URL sources)
```{r}
library(readxl)

excel_path <- "\\\\kt.ktzh.ch\\Personal\\Home01\\B117T23\\Documents\\Laura Bazzigher\\Privat\\Studium\\Riskktaking\\Data\\Hardship_complete.xlsx"
countryfacts <- read_excel(excel_path)

labels <- c("code", "country", "codeWVS", "Homicide", "GDP", "InfMort", "LifeExp", "GINI", "GenderPEdu")
names(countryfacts) <- labels

unique(data$country) %in% countryfacts$codeWVS # check that all countries in the subset of the WVS data are included in the countryfacts file

##### Haiti is not in the countryfacts list ##### countryfacts data 
```


# Plot histogram of hardship indicators and transform skewed indicators
```{r}
panel.hist = function(x)
{
  layout(matrix(c(1:6), 2, 3, byrow = TRUE))
  par(mar=c(5,5,2,1))
  labels=names(x)
  for (counter in 1:ncol(x))
  {
    if(is.numeric(x[, counter])) {
      hist(x[,counter],las=1,main=labels[counter],xlab="")
    }
  }
}

panel.hist(countryfacts[,4:9]) # plot histogram of country indicators
dev.print(postscript,"histindicators.eps",width=6, height=6,horizontal=FALSE,onefile=FALSE)
```

# log transform
```{r}
countryfacts$Homicide=log(countryfacts$Homicide)
countryfacts$GDP=log(countryfacts$GDP)
countryfacts$InfMort=log(countryfacts$InfMort)
countryfacts$LifeExp=log(countryfacts$LifeExp)
```

# scale and reverse
```{r}
countryfacts$Homicide=scale(countryfacts$Homicide)
countryfacts$GDP=scale(-countryfacts$GDP)
countryfacts$InfMort=scale(countryfacts$InfMort)
countryfacts$LifeExp=scale(-countryfacts$LifeExp)
countryfacts$GINI=scale(countryfacts$GINI)
countryfacts$GenderPEdu=scale(-countryfacts$GenderPEdu)

panel.hist(countryfacts[,4:9]) # plot histogram of country indicators
dev.print(postscript,"histindicatorstrans.eps",width=6, height=6,horizontal=FALSE,onefile=FALSE)
```

# Convert into numerical variables
#### not in the original code 
```{r}
countryfacts$Homicide <- as.numeric(countryfacts$Homicide)
countryfacts$GDP <- as.numeric(countryfacts$GDP)
countryfacts$InfMort <- as.numeric(countryfacts$InfMort)
countryfacts$LifeExp <- as.numeric(countryfacts$LifeExp)
countryfacts$GINI <- as.numeric(countryfacts$GINI)
countryfacts$GenderPEdu <- as.numeric(countryfacts$GenderPEdu)
```

# This code does not work. I do not understand why, all the variables are numeric but it always says, that they are not. Since out counrtyfacts-document has no missing values, I do not run it.```{r}
# IMPUTE hardship indicators w/ median
#```{r}
#for (counter in 5:9)
#{
#  countryfacts[is.na(countryfacts[,counter]),counter]=median(countryfacts[,counter],na.rm=TRUE)
#}
#```

```{r}
# IMPUTE hardship indicators w/ median
for (counter in 4:9) {
  # Convert the column to numeric (in case it's not already numeric)
  countryfacts[[counter]] <- as.numeric(as.character(countryfacts[[counter]]))
  
  # Replace non-numeric values with NA
  countryfacts[[counter]][!is.na(countryfacts[[counter]]) & !is.numeric(countryfacts[[counter]])] <- NA
  
  # Impute missing values with the median
  countryfacts[[counter]][is.na(countryfacts[[counter]])] <- median(countryfacts[[counter]], na.rm = TRUE)
}
```


# Create a Hardship Index 
```{r}
countryfacts$hardship=(countryfacts$Homicide+countryfacts$GDP+countryfacts$InfMort+countryfacts$LifeExp+countryfacts$GINI+countryfacts$GenderPEdu)/6
```

# SUP MATERIALS:Correlation between hardship indicators 

## Plot scatter plot matrix
```{r}
panel.cor = function(x, y, digits = 2, cex.cor, ...)
{
  usr = par("usr"); on.exit(par(usr))
  par(usr = c(0, 1, 0, 1))
  # correlation coefficient
  r = cor(x, y,use="complete.obs")
  txt = format(c(r, 0.123456789), digits = digits)[1]
  txt = paste("r= ", txt, sep = "")
  text(0.5, 0.6, txt)
  
  # p-value calculation
  p = cor.test(x, y,use="complete.obs")$p.value
  txt2 = format(c(p, 0.123456789), digits = digits)[1]
  txt2 = paste("p= ", txt2, sep = "")
  if(p<0.01) txt2 = paste("p ", "<0.01", sep = "")
  text(0.5, 0.4, txt2)
}
pairs(countryfacts[,4:10], upper.panel = panel.cor,las=1,cex.labels=.9) 
dev.print(postscript,"scatter_indicators.eps",width=8, height=8,horizontal=FALSE,onefile=FALSE)
```

## Cronbach's alpha for Hardship Indicators
```{r}
library(psych)
alpha(countryfacts[,4:9]) # calculate consistency (Cronbach's alpha) for the hardship indicators
```

# add the country label and hardship variables to the data matrix (i.e., data)
```{r}
data[,"country_lab"]=NA
data[,"hardship"]=NA
countries=unique(data$country)
for(row in 1:length(countries))
{
  data[data$country==countries[row],"country_lab"]=countryfacts[countryfacts$codeWVS==countries[row],"code"]
  
  if(!is.na(countryfacts[countryfacts$codeWVS==countries[row],"hardship"]))
  {
    data[data$country==countries[row],"hardship"]=rep(countryfacts[countryfacts$codeWVS==countries[row],"hardship"],length(sum(data$country==countries[row])))
  }
}
data$country_lab=relevel(factor(data$country_lab),ref="USA") # make USA the reference level in case we want to make direct comparisons between countries
```

# Transfrom risk item such that high values represent more risk taking
```{r}
data$risk = 6 - data$risk + 1
```

# Risk item as ordinal variable 
```{r}
data$risk_ord=data$risk 
```

# Transform risk variable into T-score (mean = 50, sd = 10)
```{r}
data$risk = 10*scale(data$risk, center=TRUE,scale=TRUE)+50
```

# MIXED-EFFECTS LINEAR MODELING 
```{r}
#library(lme4)
library(lmerTest)
```

# model0
#### intercept only model
```{r}
model0 = lmer(risk ~ 1 + (1|country),data = data)
summary_model0=summary(model0)
summary_model0
```

# model1
#### age, sex 
```{r}
model1 <- lmer(risk ~ 1 + scale(age) + factor(sex) + (1 + scale(age) + factor(sex) | country), 
               data = data, 
               control = lmerControl(optimizer = "bobyqa"))
summary_model1=summary(model1)
summary_model1
```

# model2
#### age, sex, and covariates (children, marital status, employement status, education)
```{r}
model2 = lmer(risk ~ 1+scale(age)+factor(sex) + factor(children) + factor(married) + factor(employed) + factor(education)+ (1+scale(age)+factor(sex)+ factor(children) + factor(married) + factor(employed) + factor(education)|country),data = data,control=lmerControl(optCtrl=list(maxfun=100000),optimizer="bobyqa"))
summary_model2=summary(model2)
summary_model2
```

# model3
```{r}
model3 <- lmer(risk ~ 1+scale(age)*hardship+factor(sex)*hardship + factor(children) + factor(married) + factor(employed) + factor(education)+ (1+scale(age)+factor(sex)+ factor(children) + factor(married) + factor(employed) + factor(education)|country),data = data,control=lmerControl(optCtrl=list(maxfun=100000),optimizer="bobyqa"),REML = FALSE)
summary_model3=summary(model3)
summary_model3
```

# ANOVA
```{r}
anova(model0,model1)
anova(model1,model2)
anova(model2,model3)
```

```{r}
coefsallmodels=rbind(summary_model1$coefficients,
summary_model2$coefficients,
summary_model3$coefficients[c(1:2,4:8,3,9:10),])

write.csv(coefsallmodels,"coefsallmodels.csv")
```


#```{r}
library("wordcloud")
library(lme4)

# use scatterplots to plot correlations between hardship index and random effect estimates from Model 2 (without hardship as predictor)
modelcoefs=ranef(model2)$country
modelcoefs$codeWVS=row.names(modelcoefs)
regiondata=merge(modelcoefs,countryfacts,by="codeWVS") # merge matrices to include the hardship composite
```

#```{r}
library(wordcloud) # this helps with the display of the text labels cf. textplot() function below
plot.fit=function(x,y,xlab,ylab,labels,coef,ylims)
{
  y=y+coef # put random effects on the same scale as the fixed effects
  plot(x,y,xlab=xlab,ylab=ylab,las=1,pch=21,bg="grey",col="grey",cex=.5,cex.axis=.7,xlim=c(-2,2),ylim=ylims,bty="n")

  model=lm(y~x)
  abline(model,lwd=2,col="grey")
  r2=summary(model)$r.squared
  fstatistic=summary(model)$fstatistic
  p=pf(fstatistic[1], fstatistic[2], fstatistic[3],lower.tail=F)
  n=sum(!is.na(x))
  mylabel1 = bquote(italic(R)^2 == .(format(r2, digits = 1)))
  mylabel2 = bquote(italic(p) == .(format(p, digits = 1)))
  mylabel3 = bquote(italic(N) == .(format(n, digits = 1)))
  legend("topleft", bty="n", legend= mylabel1,text.col="black",cex=1.2)
  #legend("bottom", bty="n", legend= mylabel2,text.col="black",cex=.8,xjust=0)
  #legend("bottomleft", bty="n", legend= mylabel3,text.col="black",cex=.8)
  #text(x,y,labels=labels,cex=.8)
  textplot(x,y,labels,new=FALSE,col="black",show.lines=FALSE,ylim=ylims,cex=.6)
}
layout(matrix(c(1:3), 1, 3, byrow = TRUE))
par(mar=c(5,5,1,1))
coefs=fixef(model2)
plot.fit(regiondata$hardship,regiondata[,2],"Hardship","Intercept",regiondata$code2,coefs[1],c(46,58))
plot.fit(regiondata$hardship,regiondata[,3],"Hardship","Age Effect",regiondata$code2,coefs[2],c(-3,.5))
plot.fit(regiondata$hardship,regiondata[,4],"Hardship","Sex Effect",regiondata$code2,coefs[3],c(-5,0))
```

#```{r}
data$education_cat[education < 3] = "incomplete or no primary education"
```
