---
title: "R Notebook"
output: html_notebook
---

```{r}
rm(list = ls())
```


# Libraries
```{r}
library(data.table)
library(tidyr)
library(maps)
library(haven)
library(ggplot2)
library(dplyr)
library(readxl)
library(ggrepel)
library(wordcloud)
library(lme4)
library(lmerTest)
library(reshape2)
library(patchwork)
library(psych)
```

####################
PREP THE DATASET FOR ANALYSIS WVS 5 & 6
####################

#read the data (Wave 5)
```{r}
# Data of Wave 5
WV5_data <- readRDS("/Users/laurabazzigher/Documents/GitHub/risk_wvs/data/dataset/WV6_dataset_wave_5_6/F00007944-WV5_Data_R_v20180912.rds")

# Convert WV5_data-object in data.frame 
WV5_data_df <- as.data.frame(WV5_data)

# show first five columns
WV5_data_df
```

# clean the data set
```{r}
#rename the variables
WV5_data <- WV5_data_df %>%
  rename(gender = V235, age = V237, country_code = V2, wave = V1, risktaking = V86, children = V56, married = V55, employed = V241, education = V238)
WV5_data

colnames(WV5_data)

#select only the variables of interest
WV5_data <- WV5_data %>%
  dplyr::select(gender, age, country_code, wave, risktaking, children, employed, education, married)
WV5_data
```
# Read countrynames data from the CSV file (to decode the dataset 5)
```{r}
countrynames <- read.csv("/Users/laurabazzigher/Documents/GitHub/risk_wvs/data/dataset/WV6_dataset_wave_5_6/countrynames.txt", header = FALSE, as.is = TRUE)
colnames(countrynames) <- c("code", "name")

# Assuming WV5_data has a column named country_code
WV5_data$country <- countrynames$name[match(WV5_data$country_code, countrynames$code)]

# Check the frequency of each country in the new column
table(WV5_data$country)

# Display the updated WV5_data
print(WV5_data)
```

#control wave 5
```{r}
length(unique(WV5_data$country)) 
nrow(WV5_data) # number of individuals 
range(WV5_data$age) 
table(WV5_data$gender) # sex table(data$sex)/nrow(data) 
```
#Read Dataset (Wave 6)
```{r}
load("/Users/laurabazzigher/Documents/GitHub/risk_wvs/data/dataset/WV6_dataset_wave_5_6/WV6_Data_R_v20201117.rdata") 
WV6_data <- WV6_Data_R_v20201117 

print(WV6_data)
```
#rename variables
```{r}
WV6_data <- WV6_data %>%
  rename(wave = V1, gender = V240, age = V242,country_code = V2, risktaking = V76, children = V58, married = V57, employed = V229, education = V248)

#select only the variables of interest
WV6_data <- WV6_data %>%
  dplyr::select(gender, age, country_code, wave, risktaking, children, employed, education, married)
WV6_data
```
#decode daraset (Wave 6)
```{r}
countrynames = read.csv("/Users/laurabazzigher/Documents/GitHub/risk_wvs/data/dataset/WV6_dataset_wave_5_6/countrynames.txt", header=FALSE,as.is=TRUE)
colnames(countrynames) = c("code", "name")
WV6_data$country = countrynames$name [match(WV6_data$country_code, countrynames$code)]
table(WV6_data$country)
WV6_data
```
#control wave 6
```{r}
length(unique(WV6_data$country)) 
nrow(WV6_data) # number of individuals  
range(WV6_data$age, na.rm = TRUE)
table(WV6_data$gender) # sex table(data$sex)/nrow(data) 
```


#combine the 2 dataset (Wave 6 + Wave 5)
```{r}
WVS_data = rbind(WV5_data, WV6_data)
WVS_data
```

```{r}
length(unique(WVS_data$country)) 
nrow(WVS_data) # number of individuals 
range(WVS_data$age, na.rm=TRUE) 
table(WVS_data$gender) # sex table(data$sex)/nrow(data) 
```



#exclusion of participants and omission of missing data (na)
```{r}
WVS_data = subset(WVS_data, risktaking > 0 & gender > 0 & age >0 & education > 0 & employed > 0 & married > 0 & children >= 0)
### WVS_data <- na.omit(WVS_data) ### excluded because it is not in code from Mata et al., 2016

# Use the mutate function to change the country name
WVS_data <- WVS_data %>%
  mutate(country = ifelse(country == "Great Britain", "United Kingdom", country))
```

```{r}
length(unique(WVS_data$country)) 
nrow(WVS_data) # number of individuals 
range(WVS_data$age, na.rm=TRUE) 
table(WVS_data$gender) # sex table(data$sex)/nrow(data) 
```

# create a categorical education variable (with fewer categories than the original)
```{r}
# Neue Spalte 'education_cat' erstellen und initialisieren
WVS_data$education_cat <- NA

# Kategorien zuweisen basierend auf den Bildungsstufen
WVS_data$education_cat <- ifelse(WVS_data$education %in% c(1, 2), "incomplete or no primary education", 
                          ifelse(WVS_data$education %in% c(3, 4, 5, 6), "No Uni",
                          ifelse(WVS_data$education %in% c(7, 8, 9), "Uni", NA)))

# Tabelle der neuen Kategorien anzeigen
table(WVS_data$education_cat)
```

#Transformation of item risktaking
```{r}
# Transfrom risk item such that high values represent more risk taking
WVS_data$risktaking = 6 - WVS_data$risktaking + 1

# Transform risk variable into T-score (mean = 50, sd = 10)
WVS_data$T_score_risktaking = 10*scale(WVS_data$risktaking, center=TRUE,scale=TRUE)+50

WVS_data

#Transform risk variable into Z score 
# Assuming T-scores have a mean of 50 and a standard deviation of 10
#WVS_data$Z_score_risktaking = (WVS_data$T_score_risktaking - 50) / 10

# Print the resulting data frame
print(WVS_data)

WVS_data <- WVS_data %>%
  group_by(country) %>%
  mutate(z_score_age = scale(age))
WVS_data
```

# Dichotomizing Variables: This helps estimating and interpreting the models later on...
```{r}
WVS_data$gender = ifelse(WVS_data$gender == 1, 0, 1) # sex: male vs. female
WVS_data$children = ifelse(WVS_data$children == 0, 0, 1) # children: no vs. yes
WVS_data$married = ifelse(WVS_data$married == 1, 1, 0) # married: yes vs. no
WVS_data$employed = ifelse(WVS_data$employed < 4, 1, 0) # employed: yes vs. no
WVS_data$education = ifelse(WVS_data$education < 4, 0, 1) # education: no primary vs. primary+ 
head(WVS_data)
```
# Control the data
```{r}
length(unique(WVS_data$country))
nrow(WVS_data)
range(WVS_data$age)
table(WVS_data$gender)

table(WVS_data$children)
table(WVS_data$married)
table(WVS_data$employed)
table(WVS_data$education)
```


####################
PREP THE DATASET FOR ANALYSIS HARDSHIP
####################

```{r}
head(WVS_data)
```

# read in file that contains hardship indicators manually collected from CIA factbook, WHO, and World Bank 
```{r}
csv_path <- "/Users/laurabazzigher/Documents/GitHub/risk_wvs/data/Data_Mata_et_al._2016/countryfacts_selection_new.csv"
countryfacts <- read.csv(csv_path, as.is = TRUE, header = TRUE) 


labels=c("code","country","codeWVS","Homicide","GDP","InfMort","LifeExp","GINI","GenderPEdu")
names(countryfacts)=labels

missings=colSums(is.na(countryfacts[,4:9]))/77 # proportion of missing values for each of the hardship indicators

unique(WVS_data$country_code) %in% countryfacts$codeWVS # check that all countries in the subset of the WVS data are included in the countryfacts file

countryfacts
```

# Controll Countryfacts
```{r}
# Zeige eindeutige Werte für jede Spalte in countryfacts an
for (col in names(countryfacts)) {
  unique_values <- unique(countryfacts[[col]])
  cat("Unique values for column", col, ":", "\n")
  for (val in unique_values) {
    cat(val, "\n")
  }
  cat("\n")
}
```


# Plot histogram of all hardship indicators
```{r}
# Plot histogram of all hardship indicators
combined_plot <- NULL # Leeres Plot-Objekt erstellen

# Define the vector of labels for the items
items <- c("Homicide","GDP","InfMort","LifeExp","GINI","GenderPEdu")

# Loop durch jedes Item und füge das Histogramm zum kombinierten Plot hinzu
for (item in items) {
  # Erstelle ein Histogramm für das aktuelle Item
  plot <- ggplot(countryfacts, aes_string(x = item)) +
    geom_histogram(binwidth = 1, fill = "skyblue", color = "black") +
    labs(title = paste(item),
         x = item,
         y = "Frequency") +
    theme_minimal()
  
  # Füge das Histogramm zum kombinierten Plot hinzu
  if (is.null(combined_plot)) {
    combined_plot <- plot
  } else {
    combined_plot <- combined_plot + plot
  }
}

# Zeige den kombinierten Plot an
combined_plot
```


# log transform
```{r}
countryfacts$Homicide=log(countryfacts$Homicide)
countryfacts$GDP=log(countryfacts$GDP)
countryfacts$InfMort=log(countryfacts$InfMort)
countryfacts$LifeExp=log(countryfacts$LifeExp)
#countryfacts$GINI=log(countryfacts$GINI) # not transformed
countryfacts$GenderPEdu=log(countryfacts$GenderPEdu)

countryfacts
```

# changing variables into the same direction
```{r}
# Reverse Codierung
countryfacts$Homicide=scale(countryfacts$Homicide)
countryfacts$GDP=scale(-countryfacts$GDP)
countryfacts$InfMort=scale(countryfacts$InfMort)
countryfacts$LifeExp=scale(-countryfacts$LifeExp)
countryfacts$GINI=scale(countryfacts$GINI)
countryfacts$GenderPEdu=scale(-countryfacts$GenderPEdu)

countryfacts
```



# Create the 'hardship' column in the 'hardship' data frame
```{r}
countryfacts$hardship <- rowMeans(countryfacts[, c("Homicide", "GDP", "GINI", "LifeExp", "InfMort", "GenderPEdu")], na.rm = TRUE)

countryfacts
```

# Plot histogram of all hardship indicators after log transform
```{r}
# Plot histogram of all hardship indicators after log transform
# Leeres Plot-Objekt erstellen
combined_plot <- NULL

# Define the vector of labels for the items
items <- c("Homicide", "GDP", "GINI", "LifeExp", "InfMort", "GenderPEdu", "hardship")

# Loop durch jedes Item und füge das Histogramm zum kombinierten Plot hinzu
for (item in items) {
  # Erstelle ein Histogramm für das aktuelle Item
  plot <- ggplot(countryfacts, aes_string(x = item)) +
    geom_histogram(binwidth = 1, fill = "skyblue", color = "black") +
    labs(title = paste(item),
         x = item,
         y = "Frequency") +
    theme_minimal()
  
  # Füge das Histogramm zum kombinierten Plot hinzu
  if (is.null(combined_plot)) {
    combined_plot <- plot
  } else {
    combined_plot <- combined_plot + plot
  }
}

# Zeige den kombinierten Plot an
combined_plot
```


#################################################
# SUP MATERIALS:Correlation between hardship indicators 
# heat map 
```{r}
panel.cor = function(x, y, digits = 2, cex.cor, ...)
{
  usr = par("usr"); on.exit(par(usr))
  par(usr = c(0, 1, 0, 1))
  # correlation coefficient
  r = cor(x, y,use="complete.obs")
  txt = format(c(r, 0.123456789), digits = digits)[1]
  txt = paste("r= ", txt, sep = "")
  text(0.5, 0.6, txt)
  
  # p-value calculation
  p = cor.test(x, y,use="complete.obs")$p.value
  txt2 = format(c(p, 0.123456789), digits = digits)[1]
  txt2 = paste("p= ", txt2, sep = "")
  if(p<0.01) txt2 = paste("p ", "<0.01", sep = "")
  text(0.5, 0.4, txt2)
}
pairs(countryfacts[,4:10], upper.panel = panel.cor,las=1,cex.labels=.9) 
dev.print(postscript,"scatter_indicators.eps",width=8, height=8,horizontal=FALSE,onefile=FALSE)
```

# Cronbach's Alpha for Hardship Indicators
```{r}
library(psych)

# Subset der Hardship-Indikatoren aus dem countryfacts-Datensatz auswählen
hardship_subset <- countryfacts[, c("Homicide", "GDP", "InfMort", "LifeExp", "GINI", "GenderPEdu")]

# Cronbach's Alpha berechnen
alpha_result <- alpha(hardship_subset)
alpha_result
```

```{r}
# Ersetzen Sie "USA" durch "United States" im countryfacts-Datensatz
countryfacts$country[countryfacts$country == "USA"] <- "United States"
```

# Merge the data matrix with the countryfacts dataset based on the country code
```{r}
# Merge data from WVS_data and countryfacts
data <- merge(WVS_data, countryfacts[, c("codeWVS", "country", "Homicide", "GDP", "InfMort", "LifeExp", "GINI", "GenderPEdu", "hardship")], 
              by.x = "country_code", by.y = "codeWVS", all.x = TRUE)

# Remove the redundant column 'country_code'
data <- data[, -which(names(data) == "country_code")]

# Set USA as the reference country
if ("United States" %in% data$country) {
  data$country <- factor(data$country, levels = c("United States", unique(data$country)[!data$country %in% "United States"]))
} else {
  # If "United States" is not found, keep the country variable as is
  print("Warning: 'United States' not found in the country variable.")
}

# Display the updated data matrix
print(data)
```

```{r}
# List all unique countries in the WVS_data dataset
unique_countries <- unique(data$country)

# Display the list of unique countries
print(unique_countries)
```
####################
PREP THE DATASET FOR ANALYSIS MIXED-MODELS
####################

#Add Hardship to WVS_data
```{r}
head(WVS_data)
```
# Combine WVS_data with the hardship
```{r}
WVS_mixed_model <- left_join(WVS_data, hardship, by = "country")
WVS_mixed_model
```
# Add Hardship to gps_data
```{r}
gps_mixed_model <- left_join(gps_data, hardship, by = "country")
gps_mixed_model
```
####################
####################
####################
MIXED-MODELS 
####################
####################
####################

####################
MIXED-MODELS WVS-DATA
####################

# Mixed-model WVS - Replication of Mata et al., 2016
# intercept only model
```{r}
model0 = lmer(risktaking ~ 1 + (1|country),data = WVS_mixed_model)
summary_model0=summary(model0)
```

# age, sex 
```{r}
model1 <- lmer(risktaking ~ 1 + scale(z_score_age) + factor(gender) + (1 + scale(z_score_age) + factor(gender) | country), 
               data = WVS_mixed_model, 
                      control = lmerControl(optimizer = "bobyqa"))
```

# Koeffizientenübersicht des Modells anzeigen
```{r}
print(summary_model1)
```

```{r}
# Zusammenfassung des Modells anzeigen
summary_model1 <- summary(model1)

# Gewünschte Werte extrahieren und formatieren
results_model1 <- data.frame(
  Predictor = c("Intercept", "Age", "Gender"),
  Estimate = c(summary_model1$coefficients["(Intercept)", "Estimate"],
               summary_model1$coefficients["scale(z_score_age)", "Estimate"],
               summary_model1$coefficients["factor(gender)1", "Estimate"]),
  SE = c(summary_model1$coefficients["(Intercept)", "Std. Error"],
          summary_model1$coefficients["scale(z_score_age)", "Std. Error"],
          summary_model1$coefficients["factor(gender)1", "Std. Error"]),
  T_score = c(summary_model1$coefficients["(Intercept)", "t value"],
              summary_model1$coefficients["scale(z_score_age)", "t value"],
              summary_model1$coefficients["factor(gender)1", "t value"]),
  p_value = c(summary_model1$coefficients["(Intercept)", "Pr(>|t|)"],
              summary_model1$coefficients["scale(z_score_age)", "Pr(>|t|)"],
              summary_model1$coefficients["factor(gender)1", "Pr(>|t|)"])
)

# Formatierung der p-Werte
results_model1$p_value <- ifelse(results_model1$p_value < 0.001, "< .001", sprintf("%.3f", results_model1$p_value))

# Ergebnisse anzeigen
print(results_model1)
```
# age, sex, and covariates (children, marital status, employement status, education)
```{r}
model2 = lmer(risktaking ~ 1+scale(z_score_age)+factor(gender) + factor(children) + factor(married) + factor(employed) + factor(education)+ (1+scale(z_score_age)+factor(gender)+ factor(children) + factor(married) + factor(employed) + factor(education)|country),data = WVS_mixed_model,control=lmerControl(optCtrl=list(maxfun=30000),optimizer="bobyqa"))
summary_model2=summary(model2)
```

# Koeffizientenübersicht des Modells anzeigen
```{r}
print(summary_model2)
```
```{r}
# Zusammenfassung des Modells anzeigen
summary_model2 <- summary(model2)

# Gewünschte Werte extrahieren und formatieren
results_model2 <- data.frame(
  Predictor = c("Intercept", "Age", "Gender", "Parental status", "Marital status", "Occupational status", "Education"),
  Estimate = c(summary_model2$coefficients["(Intercept)", "Estimate"],
               summary_model2$coefficients["scale(z_score_age)", "Estimate"],
               summary_model2$coefficients["factor(gender)1", "Estimate"],
               summary_model2$coefficients["factor(children)1", "Estimate"],
               summary_model2$coefficients["factor(married)1", "Estimate"],
               summary_model2$coefficients["factor(employed)1", "Estimate"],
               summary_model2$coefficients["factor(education)1", "Estimate"]),
  SE = c(summary_model2$coefficients["(Intercept)", "Std. Error"],
          summary_model2$coefficients["scale(z_score_age)", "Std. Error"],
          summary_model2$coefficients["factor(gender)1", "Std. Error"],
          summary_model2$coefficients["factor(children)1", "Std. Error"],
          summary_model2$coefficients["factor(married)1", "Std. Error"],
          summary_model2$coefficients["factor(employed)1", "Std. Error"],
          summary_model2$coefficients["factor(education)1", "Std. Error"]),
  T_score = c(summary_model2$coefficients["(Intercept)", "t value"],
              summary_model2$coefficients["scale(z_score_age)", "t value"],
              summary_model2$coefficients["factor(gender)1", "t value"],
              summary_model2$coefficients["factor(children)1", "t value"],
              summary_model2$coefficients["factor(married)1", "t value"],
              summary_model2$coefficients["factor(employed)1", "t value"],
              summary_model2$coefficients["factor(education)1", "t value"]),
  p_value = c(summary_model2$coefficients["(Intercept)", "Pr(>|t|)"],
              summary_model2$coefficients["scale(z_score_age)", "Pr(>|t|)"],
              summary_model2$coefficients["factor(gender)1", "Pr(>|t|)"],
              summary_model2$coefficients["factor(children)1", "Pr(>|t|)"],
              summary_model2$coefficients["factor(married)1", "Pr(>|t|)"],
              summary_model2$coefficients["factor(employed)1", "Pr(>|t|)"],
              summary_model2$coefficients["factor(education)1", "Pr(>|t|)"])
)

# Formatierung der p-Werte
results_model2$p_value <- ifelse(results_model2$p_value < 0.001, "< .001", sprintf("%.3f", results_model2$p_value))

# Ergebnisse anzeigen
print(results_model2)
```

```{r}
model3 <- lmer(risktaking ~ 1+scale(z_score_age)*hardship+factor(gender)*hardship + factor(children) + factor(married) + factor(employed) + factor(education)+ (1+scale(z_score_age)+factor(gender)+ factor(children) + factor(married) + factor(employed) + factor(education)|country),data = WVS_mixed_model,control=lmerControl(optCtrl=list(maxfun=30000),optimizer="bobyqa"),REML = FALSE)
summary_model3=summary(model3)
```

# Koeffizientenübersicht des Modells anzeigen
```{r}
print(summary_model3)
```
# Zusammenfassung des Modells anzeigen
```{r}
# Zusammenfassung des Modells anzeigen
summary_model3 <- summary(model3)

# Gewünschte Werte extrahieren und formatieren
results_model3 <- data.frame(
  Predictor = c("Intercept", "Age", "Gender", "Parental status", "Marital status", "Occupational status", "Education", "Hardship", "Interaction: Gender * Hardship"),
  Estimate = c(summary_model3$coefficients["(Intercept)", "Estimate"],
               summary_model3$coefficients["scale(z_score_age)", "Estimate"],
               summary_model3$coefficients["factor(gender)1", "Estimate"],
               summary_model3$coefficients["factor(children)1", "Estimate"],
               summary_model3$coefficients["factor(married)1", "Estimate"],
               summary_model3$coefficients["factor(employed)1", "Estimate"],
               summary_model3$coefficients["factor(education)1", "Estimate"],
               summary_model3$coefficients["hardship", "Estimate"],
               summary_model3$coefficients["hardship:factor(gender)1", "Estimate"]),
  SE = c(summary_model3$coefficients["(Intercept)", "Std. Error"],
          summary_model3$coefficients["scale(z_score_age)", "Std. Error"],
          summary_model3$coefficients["factor(gender)1", "Std. Error"],
          summary_model3$coefficients["factor(children)1", "Std. Error"],
          summary_model3$coefficients["factor(married)1", "Std. Error"],
          summary_model3$coefficients["factor(employed)1", "Std. Error"],
          summary_model3$coefficients["factor(education)1", "Std. Error"],
          summary_model3$coefficients["hardship", "Std. Error"],
          summary_model3$coefficients["hardship:factor(gender)1", "Std. Error"]),
  T_score = c(summary_model3$coefficients["(Intercept)", "t value"],
              summary_model3$coefficients["scale(z_score_age)", "t value"],
              summary_model3$coefficients["factor(gender)1", "t value"],
              summary_model3$coefficients["factor(children)1", "t value"],
              summary_model3$coefficients["factor(married)1", "t value"],
              summary_model3$coefficients["factor(employed)1", "t value"],
              summary_model3$coefficients["factor(education)1", "t value"],
              summary_model3$coefficients["hardship", "t value"],
              summary_model3$coefficients["hardship:factor(gender)1", "t value"]),
  p_value = c(summary_model3$coefficients["(Intercept)", "Pr(>|t|)"],
              summary_model3$coefficients["scale(z_score_age)", "Pr(>|t|)"],
              summary_model3$coefficients["factor(gender)1", "Pr(>|t|)"],
              summary_model3$coefficients["factor(children)1", "Pr(>|t|)"],
              summary_model3$coefficients["factor(married)1", "Pr(>|t|)"],
              summary_model3$coefficients["factor(employed)1", "Pr(>|t|)"],
              summary_model3$coefficients["factor(education)1", "Pr(>|t|)"],
              summary_model3$coefficients["hardship", "Pr(>|t|)"],
              summary_model3$coefficients["hardship:factor(gender)1", "Pr(>|t|)"])
)

# Formatierung der p-Werte
results_model3$p_value <- ifelse(results_model3$p_value < 0.001, "< .001", sprintf("%.3f", results_model3$p_value))

# Ergebnisse anzeigen
print(results_model3)
```

```{r}
anova(model0,model1)
anova(model1,model2)
anova(model2,model3) 
```

```{r}
coefsallmodels=rbind(summary_model1$coefficients,
summary_model2$coefficients,
summary_model3$coefficients[c(1:2,4:8,3,9:10),])

write.csv(coefsallmodels,"coefsallmodels.csv")
```

# Delete when submitting the code --> just for me to know where the document is
```{r}
file_path <- file.path(getwd(), "coefsallmodels.csv")
file_path
```

```{r}
# Extrahieren der Koeffizienten-Tabelle für jedes Modell
coefficients_model0 <- summary(model0)$coefficients
coefficients_model1 <- summary(model1)$coefficients
coefficients_model2 <- summary(model2)$coefficients
coefficients_model3 <- summary(model3)$coefficients

# Filtern der erforderlichen Zeilen aus den Koeffizienten
coefficients_model0 <- coefficients_model0[rownames(coefficients_model0) %in% c("(Intercept)", "scale(z_score_age)", "factor(gender)"), ]
coefficients_model1 <- coefficients_model1[rownames(coefficients_model1) %in% c("(Intercept)", "scale(z_score_age)", "factor(gender)"), ]
coefficients_model2 <- coefficients_model2[rownames(coefficients_model2) %in% c("(Intercept)", "scale(z_score_age)", "factor(gender)", "factor(children)", "factor(married)", "factor(employed)", "factor(education)"), ]
coefficients_model3 <- coefficients_model3[rownames(coefficients_model3) %in% c("(Intercept)", "scale(z_score_age)", "factor(gender)", "factor(children)", "factor(married)", "factor(employed)", "factor(education)", "hardship", "scale(z_score_age):hardship", "factor(gender):hardship"), ]

# Zusammenführen der geschätzten Koeffizienten aus allen Modellen
coefs_all_models <- rbind(coefficients_model0, coefficients_model1, coefficients_model2, coefficients_model3)

# Erstellen einer Tabelle aus den Koeffizienten
results_table <- data.frame(
  Predictor = rownames(coefs_all_models),
  b = coefs_all_models[, "Estimate"],
  SE = coefs_all_models[, "Std. Error"],
  T_score = coefs_all_models[, "t value"],
  p_value = coefs_all_models[, "Pr(>|t|)"]
)

# Drucken der Ergebnistabelle
results_table
```



