---
title: "R Notebook"
output: html_notebook
---

```{r}
library(data.table)
library(tidyr)
library(maps)
library(haven)
library(ggplot2)
library(dplyr)
library(readxl)
library(ggrepel)
library(wordcloud)
library(lme4)
library(lmerTest)
library(reshape2)
```

####################
####################
####################
PREPARATION DATASETS FOR ANALYSIS
####################
####################
####################

####################
PREP THE DATASET FOR ANALYSIS WVS 5 & 6
####################

#read the data (Wave 5)
```{r}
# Data of Wave 5
WV5_data <- readRDS("/Users/laurabazzigher/Documents/GitHub/risk_wvs/data/dataset/WV6_dataset_wave_5_6/F00007944-WV5_Data_R_v20180912.rds")

# Convert WV5_data-object in data.frame 
WV5_data_df <- as.data.frame(WV5_data)

# show first five columns
WV5_data_df
```

# clean the data set
```{r}
#rename the variables
WV5_data <- WV5_data_df %>%
  rename(gender = V235, age = V237, country_code = V2, wave = V1, risktaking = V86, children = V56, married = V55, employed = V241, education = V238)
WV5_data

colnames(WV5_data)

#select only the variables of interest
WV5_data <- WV5_data %>%
  dplyr::select(gender, age, country_code, wave, risktaking, children, employed, education, married)
WV5_data
```
# Read countrynames data from the CSV file (to decode the dataset 5)
```{r}
countrynames <- read.csv("/Users/laurabazzigher/Documents/GitHub/risk_wvs/data/dataset/WV6_dataset_wave_5_6/countrynames.txt", header = FALSE, as.is = TRUE)
colnames(countrynames) <- c("code", "name")

# Assuming WV5_data has a column named country_code
WV5_data$country <- countrynames$name[match(WV5_data$country_code, countrynames$code)]

# Check the frequency of each country in the new column
table(WV5_data$country)

# Display the updated WV5_data
print(WV5_data)
```
#Read Dataset (Wave 6)
```{r}
WV6_data <- load("/Users/laurabazzigher/Documents/GitHub/risk_wvs/data/dataset/WV6_dataset_wave_5_6/WV6_Data_R_v20201117.rdata") 
WV6_data <- WV6_Data_R_v20201117 
print(WV6_data)
```
#rename variables
```{r}
WV6_data <- WV6_data %>%
  rename(wave = V1, gender = V240, age = V242,country_code = V2, risktaking = V76, children = V58, married = V57, employed = V229, education = V248)

#select only the variables of interest
WV6_data <- WV6_data %>%
  dplyr::select(gender, age, country_code, wave, risktaking, children, employed, education, married)
WV6_data
```
#decode daraset (Wave 6)
```{r}
countrynames = read.csv("/Users/laurabazzigher/Documents/GitHub/risk_wvs/data/dataset/WV6_dataset_wave_5_6/countrynames.txt", header=FALSE,as.is=TRUE)
colnames(countrynames) = c("code", "name")
WV6_data$country = countrynames$name [match(WV6_data$country_code, countrynames$code)]
table(WV6_data$country)
WV6_data
```


#combine the 2 dataset (Wave 6 + Wave 5)
```{r}
WV5_data
WV6_data
WVS_data = rbind(WV5_data, WV6_data)
WVS_data
```


#exclusion of participants and omission of missing data (na)
```{r}
WVS_data = subset(WVS_data, risktaking > 0 & gender > 0 & age >0 & education > 0 & employed > 0 & married > 0 & children >= 0)
data_Wave5 = subset(WV5_data, risktaking > 0 & gender > 0 & age >0 & education > 0 & employed > 0 & married > 0 & children >= 0)
data_Wave6 = subset(WV6_data, risktaking > 0 & gender > 0 & age >0 & education > 0 & employed > 0 & married > 0 & children >= 0)
WVS_data <- na.omit(WVS_data)
data_Wave5 <- na.omit(data_Wave5)
data_Wave6 <- na.omit(data_Wave6)

# Use the mutate function to change the country name
WVS_data <- WVS_data %>%
  mutate(country = ifelse(country == "Great Britain", "United Kingdom", country))
```

# create a categorical education variable (with fewer categories than the original)
```{r}
# Neue Spalte 'education_cat' erstellen und initialisieren
WVS_data$education_cat <- NA

# Kategorien zuweisen basierend auf den Bildungsstufen
WVS_data$education_cat <- ifelse(WVS_data$education %in% c(1, 2), "incomplete or no primary education", 
                          ifelse(WVS_data$education %in% c(3, 4, 5, 6), "No Uni",
                          ifelse(WVS_data$education %in% c(7, 8, 9), "Uni", NA)))

# Tabelle der neuen Kategorien anzeigen
table(WVS_data$education_cat)
```
#Transformation of item risktaking
```{r}
# Transfrom risk item such that high values represent more risk taking
WVS_data$risktaking = 6 - WVS_data$risktaking + 1

# Transform risk variable into T-score (mean = 50, sd = 10)
WVS_data$T_score_risktaking = 10*scale(WVS_data$risktaking, center=TRUE,scale=TRUE)+50

WVS_data

#Transform risk variable into Z score 
# Assuming T-scores have a mean of 50 and a standard deviation of 10
#WVS_data$Z_score_risktaking = (WVS_data$T_score_risktaking - 50) / 10

# Print the resulting data frame
print(WVS_data)

WVS_data <- WVS_data %>%
  group_by(country) %>%
  mutate(z_score_age = scale(age))
WVS_data
```

```{r}
length(unique(WVS_data$country)) 
nrow(WVS_data) # number of individuals --> Mata et al., 2016 N = 147,118 
range(WVS_data$age) 
table(WVS_data$gender) # sex table(data$sex)/nrow(data) --> 76,617 Female (1)
```
# Dichotomizing Variables: This helps estimating and interpreting the models later on...
```{r}
WVS_data$gender = ifelse(WVS_data$gender == 1, 0, 1) # sex: male vs. female
WVS_data$children = ifelse(WVS_data$children == 0, 0, 1) # children: no vs. yes
WVS_data$married = ifelse(WVS_data$married == 1, 1, 0) # married: yes vs. no
WVS_data$employed = ifelse(WVS_data$employed < 4, 1, 0) # employed: yes vs. no
WVS_data$education = ifelse(WVS_data$education < 4, 0, 1) # education: no primary vs. primary+ 
head(WVS_data)
```
####################
PREP THE DATASET FOR ANALYSIS GPS
####################

#Add data GPS
```{r}
gps_data <- haven::read_dta("/Users/laurabazzigher/Documents/GitHub/risk_wvs/data/dataset/GPS_dataset_individual_level/individual_new.dta")

head(gps_data)
```
# Clean the data by removing records with missing values
```{r}
gps_data <- gps_data %>%
  drop_na(country, isocode, risktaking, gender, age)

# Display the cleaned data
gps_data
```
#select only the variables of interest
```{r}
gps_data <- gps_data %>%
  dplyr::select(country, isocode, ison, risktaking, gender, age)
gps_data
```
# Transform age (z-score)
```{r}
gps_data <- gps_data %>%
  group_by(country) %>%
  mutate(z_score_age = scale(age))

# Display the new column with Z-Scores per Country
gps_data
```
####################
PREP THE DATASET FOR ANALYSIS HARDSHIP
####################

# read in file that contains hardship indicators manually collected from CIA factbook, WHO, and World Bank 
```{r}
excel_path <- "/Users/laurabazzigher/Documents/GitHub/risk_wvs/data/dataset/Hardship/Hardship_complete_2024.xlsx"
hardship <- read_excel(excel_path)

# Create a vector of labels with the same length as the number of columns in 'countryfacts'
labels <- c("country","mean_homicide","gdp","gini_income","Infant_mortality","life_expect","primary_female_enrollment_rate")

# Print the result
print(hardship)
```
# Create the 'hardship' column in the 'hardship' data frame
```{r}
# Create the 'hardship' column in the 'hardship' data frame
hardship <- hardship %>%
  mutate(hardship = (mean_homicide + gdp + gini_income + Infant_mortality + life_expect + primary_female_enrollment_rate) / 6)
hardship
```
# log transform
```{r}
hardship$mean_homicide=log(hardship$mean_homicide)
hardship$gdp=log(hardship$gdp)
hardship$Infant_mortality=log(hardship$Infant_mortality)
hardship$life_expect=log(hardship$life_expect)
hardship$gini_income=log(hardship$gini_income)
hardship$primary_female_enrollment_rate=log(hardship$primary_female_enrollment_rate)

# changing variables into the same direction

# Reverse Codierung
hardship$mean_homicide=scale(hardship$mean_homicide)
hardship$gdp=scale(-hardship$gdp)
hardship$Infant_mortality=scale(hardship$Infant_mortality)
hardship$life_expect=scale(-hardship$life_expect)
hardship$gini_income=scale(hardship$gini_income)
hardship$primary_female_enrollment_rate=scale(hardship$primary_female_enrollment_rate)

hardship
```
# create a hardship index
```{r}
hardship$hardship=(hardship$mean_homicide+hardship$gdp+hardship$gini_income+hardship$life_expect+hardship$Infant_mortality+hardship$primary_female_enrollment_rate)/6

hardship
```
#################################################
# SUP MATERIALS:Correlation between hardship indicators 
```{r}
# Berechnung der Korrelationsmatrix für den Datensatz "hardship"
correlation_hardship <- cor(hardship[, c("mean_homicide", "gdp", "gini_income", "Infant_mortality", "life_expect", "primary_female_enrollment_rate")])

correlation_hardship_melted <- melt(correlation_hardship)

ggplot(correlation_hardship_melted, aes(Var1, Var2, fill = value)) +
  geom_tile(color = "white") +
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
                       midpoint = 0, limit = c(-1,1), space = "Lab", 
                       name="Correlation") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, 
                                   size = 10, hjust = 1)) +
  coord_fixed()
```
# Berechnung der Korrelationsmatrix für den Datensatz "hardship"
```{r}
correlation_hardship <- cor(hardship[, c("mean_homicide", "gdp", "gini_income", "Infant_mortality", "life_expect", "primary_female_enrollment_rate")])

# Erstellen einer Tabelle für die Korrelationsmatrix
correlation_table <- as.data.frame(correlation_hardship)

# Anzeigen der Tabelle
print(correlation_table)
```
# Überprüfung der Länder in beiden Datensätzen
```{r}
country_check <- unique(WVS_data$country) %in% hardship$isocode
if (all(country_check)) {
  print("Alle Länder in beiden Datensätzen sind konsistent.")
} else {
  print("Es gibt inkonsistente Länder in den Datensätzen.")
}
```
#select only the variables of interest
```{r}
hardship <- hardship %>%
  dplyr::select(country, isocode, hardship)
hardship
```
####################
PREP THE DATASET FOR ANALYSIS MIXED-MODELS
####################

#Add Hardship to WVS_data
```{r}
head(WVS_data)
```
# Combine WVS_data with the hardship
```{r}
WVS_mixed_model <- left_join(WVS_data, hardship, by = "country")
WVS_mixed_model
```
# Add Hardship to gps_data
```{r}
gps_mixed_model <- left_join(gps_data, hardship, by = "country")
gps_mixed_model
```
####################
####################
####################
MIXED-MODELS 
####################
####################
####################

####################
MIXED-MODELS WVS-DATA
####################

# Mixed-model WVS - Replication of Mata et al., 2016
# intercept only model
```{r}
model0 = lmer(risktaking ~ 1 + (1|country),data = WVS_mixed_model)
summary_model0=summary(model0)
```

# age, sex 
```{r}
model1 <- lmer(risktaking ~ 1 + scale(z_score_age) + factor(gender) + (1 + scale(z_score_age) + factor(gender) | country), 
               data = WVS_mixed_model, 
                      control = lmerControl(optimizer = "bobyqa"))
```

# Koeffizientenübersicht des Modells anzeigen
```{r}
print(summary_model1)
```

```{r}
# Zusammenfassung des Modells anzeigen
summary_model1 <- summary(model1)

# Gewünschte Werte extrahieren und formatieren
results_model1 <- data.frame(
  Predictor = c("Intercept", "Age", "Gender"),
  Estimate = c(summary_model1$coefficients["(Intercept)", "Estimate"],
               summary_model1$coefficients["scale(z_score_age)", "Estimate"],
               summary_model1$coefficients["factor(gender)1", "Estimate"]),
  SE = c(summary_model1$coefficients["(Intercept)", "Std. Error"],
          summary_model1$coefficients["scale(z_score_age)", "Std. Error"],
          summary_model1$coefficients["factor(gender)1", "Std. Error"]),
  T_score = c(summary_model1$coefficients["(Intercept)", "t value"],
              summary_model1$coefficients["scale(z_score_age)", "t value"],
              summary_model1$coefficients["factor(gender)1", "t value"]),
  p_value = c(summary_model1$coefficients["(Intercept)", "Pr(>|t|)"],
              summary_model1$coefficients["scale(z_score_age)", "Pr(>|t|)"],
              summary_model1$coefficients["factor(gender)1", "Pr(>|t|)"])
)

# Formatierung der p-Werte
results_model1$p_value <- ifelse(results_model1$p_value < 0.001, "< .001", sprintf("%.3f", results_model1$p_value))

# Ergebnisse anzeigen
print(results_model1)
```
# age, sex, and covariates (children, marital status, employement status, education)
```{r}
model2 = lmer(risktaking ~ 1+scale(z_score_age)+factor(gender) + factor(children) + factor(married) + factor(employed) + factor(education)+ (1+scale(z_score_age)+factor(gender)+ factor(children) + factor(married) + factor(employed) + factor(education)|country),data = WVS_mixed_model,control=lmerControl(optCtrl=list(maxfun=30000),optimizer="bobyqa"))
summary_model2=summary(model2)
```

# Koeffizientenübersicht des Modells anzeigen
```{r}
print(summary_model2)
```
```{r}
# Zusammenfassung des Modells anzeigen
summary_model2 <- summary(model2)

# Gewünschte Werte extrahieren und formatieren
results_model2 <- data.frame(
  Predictor = c("Intercept", "Age", "Gender", "Parental status", "Marital status", "Occupational status", "Education"),
  Estimate = c(summary_model2$coefficients["(Intercept)", "Estimate"],
               summary_model2$coefficients["scale(z_score_age)", "Estimate"],
               summary_model2$coefficients["factor(gender)1", "Estimate"],
               summary_model2$coefficients["factor(children)1", "Estimate"],
               summary_model2$coefficients["factor(married)1", "Estimate"],
               summary_model2$coefficients["factor(employed)1", "Estimate"],
               summary_model2$coefficients["factor(education)1", "Estimate"]),
  SE = c(summary_model2$coefficients["(Intercept)", "Std. Error"],
          summary_model2$coefficients["scale(z_score_age)", "Std. Error"],
          summary_model2$coefficients["factor(gender)1", "Std. Error"],
          summary_model2$coefficients["factor(children)1", "Std. Error"],
          summary_model2$coefficients["factor(married)1", "Std. Error"],
          summary_model2$coefficients["factor(employed)1", "Std. Error"],
          summary_model2$coefficients["factor(education)1", "Std. Error"]),
  T_score = c(summary_model2$coefficients["(Intercept)", "t value"],
              summary_model2$coefficients["scale(z_score_age)", "t value"],
              summary_model2$coefficients["factor(gender)1", "t value"],
              summary_model2$coefficients["factor(children)1", "t value"],
              summary_model2$coefficients["factor(married)1", "t value"],
              summary_model2$coefficients["factor(employed)1", "t value"],
              summary_model2$coefficients["factor(education)1", "t value"]),
  p_value = c(summary_model2$coefficients["(Intercept)", "Pr(>|t|)"],
              summary_model2$coefficients["scale(z_score_age)", "Pr(>|t|)"],
              summary_model2$coefficients["factor(gender)1", "Pr(>|t|)"],
              summary_model2$coefficients["factor(children)1", "Pr(>|t|)"],
              summary_model2$coefficients["factor(married)1", "Pr(>|t|)"],
              summary_model2$coefficients["factor(employed)1", "Pr(>|t|)"],
              summary_model2$coefficients["factor(education)1", "Pr(>|t|)"])
)

# Formatierung der p-Werte
results_model2$p_value <- ifelse(results_model2$p_value < 0.001, "< .001", sprintf("%.3f", results_model2$p_value))

# Ergebnisse anzeigen
print(results_model2)
```

```{r}
model3 <- lmer(risktaking ~ 1+scale(z_score_age)*hardship+factor(gender)*hardship + factor(children) + factor(married) + factor(employed) + factor(education)+ (1+scale(z_score_age)+factor(gender)+ factor(children) + factor(married) + factor(employed) + factor(education)|country),data = WVS_mixed_model,control=lmerControl(optCtrl=list(maxfun=30000),optimizer="bobyqa"),REML = FALSE)
summary_model3=summary(model3)
```

# Koeffizientenübersicht des Modells anzeigen
```{r}
print(summary_model3)
```
# Zusammenfassung des Modells anzeigen
```{r}
# Zusammenfassung des Modells anzeigen
summary_model3 <- summary(model3)

# Gewünschte Werte extrahieren und formatieren
results_model3 <- data.frame(
  Predictor = c("Intercept", "Age", "Gender", "Parental status", "Marital status", "Occupational status", "Education", "Hardship", "Interaction: Gender * Hardship"),
  Estimate = c(summary_model3$coefficients["(Intercept)", "Estimate"],
               summary_model3$coefficients["scale(z_score_age)", "Estimate"],
               summary_model3$coefficients["factor(gender)1", "Estimate"],
               summary_model3$coefficients["factor(children)1", "Estimate"],
               summary_model3$coefficients["factor(married)1", "Estimate"],
               summary_model3$coefficients["factor(employed)1", "Estimate"],
               summary_model3$coefficients["factor(education)1", "Estimate"],
               summary_model3$coefficients["hardship", "Estimate"],
               summary_model3$coefficients["hardship:factor(gender)1", "Estimate"]),
  SE = c(summary_model3$coefficients["(Intercept)", "Std. Error"],
          summary_model3$coefficients["scale(z_score_age)", "Std. Error"],
          summary_model3$coefficients["factor(gender)1", "Std. Error"],
          summary_model3$coefficients["factor(children)1", "Std. Error"],
          summary_model3$coefficients["factor(married)1", "Std. Error"],
          summary_model3$coefficients["factor(employed)1", "Std. Error"],
          summary_model3$coefficients["factor(education)1", "Std. Error"],
          summary_model3$coefficients["hardship", "Std. Error"],
          summary_model3$coefficients["hardship:factor(gender)1", "Std. Error"]),
  T_score = c(summary_model3$coefficients["(Intercept)", "t value"],
              summary_model3$coefficients["scale(z_score_age)", "t value"],
              summary_model3$coefficients["factor(gender)1", "t value"],
              summary_model3$coefficients["factor(children)1", "t value"],
              summary_model3$coefficients["factor(married)1", "t value"],
              summary_model3$coefficients["factor(employed)1", "t value"],
              summary_model3$coefficients["factor(education)1", "t value"],
              summary_model3$coefficients["hardship", "t value"],
              summary_model3$coefficients["hardship:factor(gender)1", "t value"]),
  p_value = c(summary_model3$coefficients["(Intercept)", "Pr(>|t|)"],
              summary_model3$coefficients["scale(z_score_age)", "Pr(>|t|)"],
              summary_model3$coefficients["factor(gender)1", "Pr(>|t|)"],
              summary_model3$coefficients["factor(children)1", "Pr(>|t|)"],
              summary_model3$coefficients["factor(married)1", "Pr(>|t|)"],
              summary_model3$coefficients["factor(employed)1", "Pr(>|t|)"],
              summary_model3$coefficients["factor(education)1", "Pr(>|t|)"],
              summary_model3$coefficients["hardship", "Pr(>|t|)"],
              summary_model3$coefficients["hardship:factor(gender)1", "Pr(>|t|)"])
)

# Formatierung der p-Werte
results_model3$p_value <- ifelse(results_model3$p_value < 0.001, "< .001", sprintf("%.3f", results_model3$p_value))

# Ergebnisse anzeigen
print(results_model3)
```

```{r}
anova(model0,model1)
anova(model1,model2)
anova(model2,model3) 
```

```{r}
coefsallmodels=rbind(summary_model1$coefficients,
summary_model2$coefficients,
summary_model3$coefficients[c(1:2,4:8,3,9:10),])

write.csv(coefsallmodels,"coefsallmodels.csv")
```

# Delete when submitting the code --> just for me to know where the document is
```{r}
file_path <- file.path(getwd(), "coefsallmodels.csv")
file_path
```

```{r}
# Extrahieren der Koeffizienten-Tabelle für jedes Modell
coefficients_model0 <- summary(model0)$coefficients
coefficients_model1 <- summary(model1)$coefficients
coefficients_model2 <- summary(model2)$coefficients
coefficients_model3 <- summary(model3)$coefficients

# Filtern der erforderlichen Zeilen aus den Koeffizienten
coefficients_model0 <- coefficients_model0[rownames(coefficients_model0) %in% c("(Intercept)", "scale(z_score_age)", "factor(gender)"), ]
coefficients_model1 <- coefficients_model1[rownames(coefficients_model1) %in% c("(Intercept)", "scale(z_score_age)", "factor(gender)"), ]
coefficients_model2 <- coefficients_model2[rownames(coefficients_model2) %in% c("(Intercept)", "scale(z_score_age)", "factor(gender)", "factor(children)", "factor(married)", "factor(employed)", "factor(education)"), ]
coefficients_model3 <- coefficients_model3[rownames(coefficients_model3) %in% c("(Intercept)", "scale(z_score_age)", "factor(gender)", "factor(children)", "factor(married)", "factor(employed)", "factor(education)", "hardship", "scale(z_score_age):hardship", "factor(gender):hardship"), ]

# Zusammenführen der geschätzten Koeffizienten aus allen Modellen
coefs_all_models <- rbind(coefficients_model0, coefficients_model1, coefficients_model2, coefficients_model3)

# Erstellen einer Tabelle aus den Koeffizienten
results_table <- data.frame(
  Predictor = rownames(coefs_all_models),
  b = coefs_all_models[, "Estimate"],
  SE = coefs_all_models[, "Std. Error"],
  T_score = coefs_all_models[, "t value"],
  p_value = coefs_all_models[, "Pr(>|t|)"]
)

# Drucken der Ergebnistabelle
results_table
```



