---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---


```{r}
rm(list = ls())
```

# Set path Cristina: ONLY USE FOR CRISTINA
```{r}
base_path <- "/Users/cristinacandido/Documents/Github/risk_wvs/data/"
```

# Set path Laura: ONLY USE FOR LAURA 
```{r}
base_path <- "/Users/laurabazzigher/Documents/GitHub/risk_wvs/data/dataset/Data_S2/"
```

# Library 
```{r}
library(data.table)
library(tidyr)
library(maps)
library(haven)
library(ggplot2)
library(dplyr)
library(readxl)
library(dplyr)
library(lmerTest)
library(lme4)
library(broom)
library(tibble)
```

# Load Countryfacts
```{r}
countryfacts <- read_excel(paste0(base_path, "Hardship_complete_2024.xlsx"))
countryfacts
```

# Log Countryfacts 
```{r}
countryfacts$homiciderate=log(countryfacts$homiciderate)
countryfacts$gdp=log(countryfacts$gdp)
countryfacts$infantmortality=log(countryfacts$infantmortality)
countryfacts$lifeexpectancy=log(countryfacts$lifeexpectancy)

countryfacts

# Reverse Codierung
countryfacts$homiciderate=scale(countryfacts$homiciderate)
countryfacts$gdp=scale(-countryfacts$gdp)
countryfacts$infantmortality=scale(countryfacts$infantmortality)
countryfacts$lifeexpectancy=scale(-countryfacts$lifeexpectancy)
countryfacts$gini=scale(countryfacts$gini)
countryfacts$femalemale_primedu=scale(-countryfacts$femalemale_primedu)
countryfacts

countryfacts$hardship_index=(countryfacts$homiciderate+countryfacts$gdp+countryfacts$gini+countryfacts$lifeexpectancy+countryfacts$infantmortality+countryfacts$femalemale_primedu)/6

countryfacts
```

# Impute missing values in the hardship indicators using the median
```{r}
countryfacts <- countryfacts %>%
  mutate(across(c("homiciderate", "gdp", "infantmortality", "lifeexpectancy", "gini", "femalemale_primedu"),
                ~ifelse(is.na(.), median(., na.rm = TRUE), .)))

countryfacts

# Use the mutate function to change the country name
countryfacts <- countryfacts %>%
  mutate(country = ifelse(label == "Serbia and Montenegro", "Serbia", label))
countryfacts
```

# Data of Wave 5
```{r}
# Data of Wave 5
WV5_data <- readRDS(paste0(base_path, "F00007944-WV5_Data_R_v20180912.rds"))

# Convert WV5_data-object in data.frame 
WV5_data_df <- as.data.frame(WV5_data)

# show first five columns
WV5_data_df

```


#rename and select variables of interest
```{r}
data5 <- WV5_data_df %>%
  rename(gender = V235, age = V237, country_code = V2, wave = V1, risktaking = V86, children = V56, married = V55, employed = V241, education = V238)
data5

colnames(data5)

#select only the variables of interest
data5 <- data5 %>%
  dplyr::select(gender, age, country_code, wave, risktaking, children, married, employed, education)
data5

# Read countrynames data from the CSV file (to decode the dataset 5)
countrynames <- read.csv(paste0(base_path, "/countrynames.txt"), header = FALSE, as.is = TRUE)
colnames(countrynames) <- c("code", "name")

# Assuming WV5_data has a column named country_code
data5$country <- countrynames$name[match(data5$country_code, countrynames$code)]

# Check the frequency of each country in the new column
table(data5$country)

# Display the updated WV5_data
print(data5)
unique(data5$country)

print(countrynames)

country_counts <- data5 %>%
  count(country)

# Print the result
print(country_counts)
```


#Read Dataset (Wave 6)
```{r}
load(paste0(base_path, "WV6_Data_R_v20201117.rdata")) 
WV6_data <- WV6_Data_R_v20201117 
print(WV6_data)
```


#rename and select variables of interest
```{r}
data6 <- WV6_data %>%
  rename(wave = V1, gender = V240, age = V242,country_code = V2, risktaking = V76, children = V58, married = V57, employed = V229, education = V248)


#select only the variables of interest
data6 <- data6 %>%
  dplyr::select(wave, gender, age, country_code,risktaking, children, married, employed, education)
data6
```

# Load Countrynames 
```{r}
countrynames = read.csv(paste0(base_path, "countrynames.txt"), header=FALSE,as.is=TRUE)
colnames(countrynames) = c("code", "name")
data6$country = countrynames$name[match(data6$country_code, countrynames$code)]
table(data6$country)
data6
```

# Bind data5 and data6 
```{r}
data = rbind(data5, data6)
data

country_counts <- data %>%
  count(country)

# Print the result
print(country_counts)
```


# Remove missing variables 
```{r}
data = subset(data, risktaking > 0 & gender > 0 & age >0 & education > 0 & employed > 0 & married > 0 & children >= 0)
data5 = subset(data5, risktaking > 0 & gender > 0 & age >0 & education > 0 & employed > 0 & married > 0 & children >= 0)
data6 = subset(data6, risktaking > 0 & gender > 0 & age >0 & education > 0 & employed > 0 & married > 0 & children >= 0)
data <- na.omit(data)
data5 <- na.omit(data5)
data6 <- na.omit(data6)

data

# Use the mutate function to change the country name
data <- data %>%
  mutate(country = ifelse(country == "Great Britain", "United Kingdom", country))
```


# Transfrom risk item 
```{r}
# Transfrom risk item such that high values represent more risk taking
data$risktaking = 6 - data$risktaking + 1

  
# Transform risk variable into T-score (mean = 50, sd = 10)
data$risktaking = 10*scale(data$risktaking, center=TRUE,scale=TRUE)+50

data

#Transform risk variable into Z score 

#factor gender 
data$gender <- factor(data$gender)

#scale age 
data$age <- scale(data$age)

country_counts <- data %>%
  count(country)

# Print the result
print(country_counts)

data
```

# Dichotomizing variables 
```{r}
data$gender = ifelse(data$gender == 1, 0, 1) # sex: male vs. female
data$children = ifelse(data$children == 0, 0, 1) # children: no vs. yes
data$married = ifelse(data$married == 1, 1, 0) # married: yes vs. no
data$employed = ifelse(data$employed < 4, 1, 0) # employed: yes vs. no
data$education = ifelse(data$education < 4, 0, 1) # education: no primary vs. primary+ 

countryfacts


countryfacts <- countryfacts %>%
  dplyr::select(label, code, hardship_index)
countryfacts

data
```

# Create dataset for mixed-models 
```{r}
countryfacts<- rename(countryfacts, country = label)

countryfacts

mixed_model_data <- left_join(data, countryfacts, by = "country")
mixed_model_data

unique(mixed_model_data$country)
```

# Model0
```{r}
# intercept only model
model0_wvs = lmer(risktaking ~ 1 + (1|country), data = mixed_model_data)
summary_model0_wvs = summary(model0_wvs)
summary_model0_wvs
```

# Model1 (age, gender)
```{r}
mixed_model_data

# age, gender 
model1_wvs <- lmer(risktaking ~ 1 + age + gender + (1 + age + gender | country), 
                   data = mixed_model_data, 
                   control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000)))
summary_model1_wvs=summary(model1_wvs)
summary_model1_wvs

summary
```

# Model2 (age, gender, children, marital status, education, employment status)
```{r}
#model 2

# Define the lmer model and assign it to 'model_2'
mixed_model_data$children <- factor(mixed_model_data$children)
mixed_model_data$married <- factor(mixed_model_data$married)
mixed_model_data$education <- factor(mixed_model_data$education)
mixed_model_data$employed <- factor(mixed_model_data$employed)

options(scipen = 100)
model2_wvs <- lmer(risktaking ~ 1 + age + gender + children + 
                 married + education + employed +
                 (1 + age + gender + children + employed +
                  married | country),
                data = mixed_model_data, control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000)))


# Display the summary of the model
summary_model2_wvs = summary(model2_wvs)
summary_model2_wvs
```


## This code did not work for Laura, but I kept it in the code in case i made a mistake

# Model3 (age, gender, children, marital status, education, employment status, hardship)
#```{r}
options(scipen = 100)
model3_wvs <- lmer(risktaking ~ 1 + age * hardship_index + 
                    gender * hardship_index + married + children + 
                    education + employed + 
                    (1 + age + married + children + 
                     education + employed | country),
                data = mixed_model_data,control=lmerControl(optCtrl=list(maxfun=100000),optimizer="bobyqa"),REML = FALSE)

summary_model3_wvs = summary(model3_wvs) 

summary_model3_wvs
#```


```{r}
model3_wvs <- lmer(risktaking ~ 1 + age * hardship_index + gender * hardship_index + married + children + 
                   education + employed + 
                   (1 + age + married + children + education + employed | country),
                   data = mixed_model_data,
                   REML = FALSE,  # Dies ist der korrekte Ort für den REML-Parameter
                   control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000)))

summary_model3_wvs = summary(model3_wvs) 

summary_model3_wvs
```


# ANOVA
```{r}
# Define anova_results list with multiple anova() calls
anova_results <- list(
  anova(model0_wvs, model1_wvs),
  anova(model1_wvs, model2_wvs),
  anova(model2_wvs, model3_wvs)
)

anova_results

# Format ANOVA results into a tidy data frame
anova_summary <- bind_rows(lapply(anova_results, tidy), .id = "Comparison")

# Print the summary table
print(anova_summary)
```


```{r}
# Bereinigen des Datensatzes vor der Modellanpassung
mixed_model_data <- na.omit(mixed_model_data)  # Entfernen aller NA-Werte
mixed_model_data <- mixed_model_data[complete.cases(mixed_model_data), ]

# Modelle anpassen
model0_wvs <- lmer(risktaking ~ 1 + (1|country), data = mixed_model_data)
model1_wvs <- lmer(risktaking ~ 1 + age + gender + (1 + age + gender | country), 
                   data = mixed_model_data, 
                   control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000)))
model2_wvs <- lmer(risktaking ~ 1 + age + gender + children + married + education + employed +
                   (1 + age + gender + children + employed + married | country),
                   data = mixed_model_data, control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000)))
model3_wvs <- lmer(risktaking ~ 1 + age * hardship_index + gender * hardship_index + married + children + 
                   education + employed + 
                   (1 + age + married + children + education + employed | country),
                   data = mixed_model_data,
                   REML = FALSE,  # Dies ist der korrekte Ort für den REML-Parameter
                   control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000)))

# ANOVA durchführen
anova_results <- list(
  anova(model0_wvs, model1_wvs),
  anova(model1_wvs, model2_wvs),
  anova(model2_wvs, model3_wvs)
)

# Ergebnisse der ANOVA ausgeben
print(anova_results)
```



# Coefs
```{r}
coefsallmodels=rbind(summary_model1$coefficients,
summary_model_2$coefficients,
summary_model_3$coefficients[c(1:2,4:8,3,9:10),])

write.csv(coefsallmodels,"coefsallmodels.csv")

modelcoefs=ranef(model_2)$country
modelcoefs$codeWVS=row.names(modelcoefs)
regiondata=merge(modelcoefs,countryfacts,by="codeWVS") # merge matrices to include the hardship composite
```

# Plot fixed effects for all countries
```{r}
# Define the filename for the PDF
pdf("fixed_effects_plot_all_countries.pdf", width = 10, height = 8)  # Adjust width and height as needed

# Plot fixed effects for all countries
smoothScatter(mixed_model_data$age, mixed_model_data$risktaking, las=1, xaxt="n", yaxt="n", 
               xlab="Age", ylab="Risk-Taking Propensity", bty="n", 
               main="ALL", cex.main=0.8, nrpoints=0, 
               xlim=c(15,85), ylim=c(35,69), cex.lab=0.6)

# Add axes and labels
axis(1, at=c(15, 85), labels=c("15", "85"), cex.axis=0.7, tck=-0.01, line=0, mgp=c(3, 0.02, 0))
axis(2, at=c(35, 65), labels=c(35, 65), las=1, cex.axis=0.7, tck=-0.01, line=0, mgp=c(3, 0.3, 0))
mtext("Age", 1, line=0, cex=0.5)
mtext(expression(Risk~Taking~(italic(T)-score)), 2, line=1, cex=0.5)
text(73, 68, "All Countries")

# Retrieve coefficients
coefs <- fixef(model_2)

# Define regression lines
regline <- function(x) {
  coefs[1] + coefs[2] * x + coefs[4] * 0.5 + coefs[5] * 0.5 + coefs[6] * 0.5 + coefs[7] * 0.5
}
lines(mean(mixed_model_data$age) + seq(-3, 3, 0.1) * sd(mixed_model_data$age), 
      regline(seq(-3, 3, 0.1)), lty=1, lwd=3, col="red")
regline <- function(x) {
  coefs[1] + coefs[2] * x + coefs[3] + coefs[4] * 0.5 + coefs[5] * 0.5 + coefs[6] * 0.5 + coefs[7] * 0.5
}
lines(mean(mixed_model_data$age) + seq(-3, 3, 0.1) * sd(mixed_model_data$age), 
      regline(seq(-3, 3, 0.1)), lty=2, lwd=3, col="red")

# Close the PDF device
dev.off()
```

# Plot fixed effects for all countries
```{r}
data$gender <- factor(data$gender)

# Create the ggplot object
my_plot <- ggplot(data, aes(x = age)) + 
  geom_density(aes(fill = gender), alpha = 0.5) + 
  scale_fill_manual(values = c("blue", "red")) +
  facet_wrap(~ country, scales = "free_y", ncol = 4) + 
  geom_smooth(aes(x = age, y = risktaking, color = gender, group = gender), method = "lm", linetype = "dashed", se = FALSE) +
  theme_minimal() +
  labs(x = "Age", y = "Propensity for Risk Taking (T score)", fill = "Age", color = "Sex") +
  theme(legend.position = "top") +
  scale_y_continuous(limits = c(30, NA)) # Set the lower limit to 30 and the upper to NA to determine it automatically

# Print the plot
print(my_plot)

# Save the plot to a PNG file
ggsave("myplot_cristina.png", my_plot, width = 10, height = 30, units = "in", dpi = 300)


data
```


```{r}
gps_data <- haven::read_dta(paste0(base_path, "individual_new.dta"))
gps_data
```


```{r}
# Clean the data by removing records with missing values
gps_data <- gps_data %>%
  drop_na(country, isocode, risktaking, gender, age)

gps_data

# Display the cleaned data
gps_data
```


```{r}
#select only the variables of interest
gps_data <- gps_data %>%
  dplyr::select(country, isocode, ison, risktaking, gender, age)
gps_data
```


```{r}
# Transform risk variable into T-score (mean = 50, sd = 10)
gps_data$risktaking = 10*scale(gps_data$risktaking, center=TRUE,scale=TRUE)+50

gps_data
```


```{r}
#factor gender 
gps_data$gender <- factor(gps_data$gender)

#scale age 
gps_data$age <- scale(gps_data$age)

gps_data

#model gps with age and gender as predictors
model1_gps = lmer(risktaking ~ 1 + age + gender + (1 + age + gender|country),data = gps_data, control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000)))
summary_model1_gps=summary(model1_gps)
summary_model1_gps
```


```{r}
countryfacts
mixed_model_gps_data <- left_join(gps_data, countryfacts, by = "country")
mixed_model_gps_data
head(mixed_model_gps_data)
```


```{r}
model2_gps <- lmer(risktaking ~ 1 + age * hardship_index + 
                    gender * hardship_index + 
                    (1 + age | country),
                data = mixed_model_gps_data,control=lmerControl(optCtrl=list(maxfun=100000),optimizer="bobyqa"),REML = FALSE)

summary_model2_gps = summary(model2_gps) 

summary_model2_gps
```


```{r}
mixed_model_gps_data
mixed_model_data

mixed_model_gps_data$source <- "gps"
mixed_model_data$source <- "data"

#select gender, age, risktaking, country, hardship_index for GPS dataset
mixed_model_gps_data_new<- mixed_model_gps_data %>%
  dplyr::select(country, gender, age, hardship_index, risktaking, source)
mixed_model_gps_data_new
mixed_model_data

#select the same variables as GPS dataset

mixed_model_data_new<- mixed_model_data %>%
  dplyr::select(country, gender, age, hardship_index, risktaking, source)

mixed_model_data_new
mixed_model_gps_data_new



mixed_model_gps_data

mixed_model_data_new
mixed_model_gps_data_new

#Combine the two datasets 

merged_data <- rbind(mixed_model_gps_data_new, mixed_model_data_new)
merged_data
```

```{r}
# Now run the mixed-effects model with source as a fixed effect
model1_combined = lmer(risktaking ~ 1 + age + gender + (1 + age + gender|country),data = gps_data, control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000)))
summary_model1_combined=summary(model1_combined)
summary_model1_combined

```

```{r}
model2_combined <- lmer(risktaking ~ 1 + age * hardship_index + 
                    gender * hardship_index + 
                    (1 + age | country),
                data = merged_data,control=lmerControl(optCtrl=list(maxfun=100000),optimizer="bobyqa"),REML = FALSE)

summary_model2_combined = summary(model2_combined) 

summary_model2_combined
```


```{r}
# Define the filename for the PDF
pdf("plot.pdf", width = 10, height = 8)  # Adjust width and height as needed

# Create a scatter plot of standardized age against risk-taking propensity with blue points
plot(merged_data$age, merged_data$risktaking, las = 1, xaxt = "n", yaxt = "n", 
     xlab = "", ylab = "Risk-Taking Propensity", bty = "n", 
     main = "ALL", cex.main = 0.8, nrpoints = 0, col = "blue",  # Set points color to blue
     xlim = c(-3, 3), ylim = c(35, 69), cex.lab = 0.6)  # Adjust xlim as needed

# Add axes and labels
axis(1, at = c(-3, 0, 3), labels = c(min(merged_data$age), 0, max(merged_data$age)), cex.axis = 0.7)
axis(2, at = c(35, 65), labels = c(35, 65), las = 1, cex.axis = 0.7, tck = -0.01, line = 0, mgp = c(3, 0.3, 0))
mtext("Age", 1, line = 0, cex = 0.5)
mtext(expression(Risk ~ Taking ~ (italic(T) - score)), 2, line = 1, cex = 0.5)
text(2.5, 68, "All Countries")

# Retrieve coefficients
coefs <- fixef(model1_combined)

# Add regression lines
abline(a = coefs[1], b = coefs[2], lty = 1, lwd = 3, col = "red")
abline(a = coefs[1] + coefs[3], b = coefs[2], lty = 2, lwd = 3, col = "red")

# Close the PDF device
dev.off()

head(merged_data)
```


