---
title: "R Notebook"
output: html_notebook
---
Variables: 

Risk
Age 
Sex
Country


```{r}
library(data.table)
library(tidyr)
library(maps)
```

#read the data (Wave 5)
```{r}
# Data of Wave 5


WV5_data <- readRDS("/Users/cristinacandido/Documents/Github/risk_wvs/data/WVS/F00007944-WV5_Data_R_v20180912.rds")


# Convert WV5_data-object in data.frame 
WV5_data_df <- as.data.frame(WV5_data)

# show first five columns
head(WV5_data_df[, 1:5])
```

# clean the data set
```{r}
library(dplyr)

#rename the variables
WV5_data <- WV5_data_df %>%
  rename(gender = V235, age = V237, country_code = V2, wave = V1, risktaking = V86)
WV5_data


#select only the variables of interest
WV5_data <- WV5_data %>%
  select(gender, age, country_code, wave, risktaking)
WV5_data
```

```{r}
#decode the country names 
countrynames = read.csv("/Users/cristinacandido/Documents/Github/risk_wvs/data/WVS/countrynames.txt", header=FALSE,as.is=TRUE)
colnames(countrynames) = c("code", "name")
WV5_data$country = countrynames$name [match(WV5_data$country_code, countrynames$code)]
table(WV5_data$country)
WV5_data


```

#Read Dataset (Wave 6)
```{r}
WV6_data <- load("/Users/cristinacandido/Documents/Github/risk_wvs/data/WVS/WV6_Data_R_v20201117.rdata") 
WV6_data <- WV6_Data_R_v20201117 
print(WV6_data)
```

#rename variables
```{r}
WV6_data <- WV6_data %>%
  rename(wave = V1, gender = V240, age = V242,country_code = V2, risktaking = V76)


#select only the variables of interest
WV6_data <- WV6_data %>%
  select(wave, gender, age, country_code,risktaking)
WV6_data

```


#decode daraset (Wave 6)
```{r}
countrynames = read.csv("/Users/cristinacandido/Documents/Github/risk_wvs/data/WVS/countrynames.txt", header=FALSE,as.is=TRUE)
colnames(countrynames) = c("code", "name")
WV6_data$country = countrynames$name [match(WV6_data$country_code, countrynames$code)]
table(WV6_data$country)
WV6_data
```

#combine the 2 dataset (Wave 6 + Wave 5)
```{r}
WV5_data
WV6_data
data = rbind(WV5_data, WV6_data)
data

#number of countries

length(unique(data$country))
```
#exclusion of participants and omission of missing data (na)
```{r}
data = subset(data, risktaking > 0 & gender > 0 & age >0 )
data_Wave5 = subset(WV5_data, risktaking > 0 & gender > 0 & age >0 )
data_Wave6 = subset(WV6_data, risktaking > 0 & gender > 0 & age >0)
data <- na.omit(data)
data_Wave5 <- na.omit(data_Wave5)
data_Wave6 <- na.omit(data_Wave6)
```
```{r}
# Transfrom risk item such that high values represent more risk taking
data$risktaking = 6 - data$risktaking + 1

  
# Transform risk variable into T-score (mean = 50, sd = 10)
data$T_score_risktaking = 10*scale(data$risktaking, center=TRUE,scale=TRUE)+50

data

#Transform risk variable into Z score 

# Assuming T-scores have a mean of 50 and a standard deviation of 10
data$Z_score_risktaking = (data$T_score_risktaking - 50) / 10

# Print the resulting data frame
print(data)

```
#World map 
```{r}
world_map <- map_data("world")
recorded_countries <- unique(data$country)
world_map$recorded <- ifelse(world_map$region %in% recorded_countries, "Recorded", "Not Recorded")

ggplot(world_map, aes(x = long, y = lat, group = group, fill = recorded)) + 
  geom_polygon(color = "white") +
  scale_fill_manual(values = c("Recorded" = "red", "Not Recorded" = "lightgrey"), guide = "none") +
  theme_void() +
  labs(title = "WVS", fill = "Status") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5))

```




```




```{r}
# Load the dplyr package
library(dplyr)

# Assuming the data frame is called 'data' and the column containing the country information is called 'country'
country_counts <- data %>%
  count(country)

# Print the result
print(country_counts)

```



#average age of participants
```{r}
mean(data$age)
median(data$age)
```

```{r}
# read in file that contains hardship indicators manually collected from CIA factbook, WHO, and World Bank 
# (see Supplemental Materials for URL sources)
countryfacts = read.csv("/Users/cristinacandido/Documents/Github/risk_wvs/data/WVS/countryfacts_selection.csv", as.is = TRUE, header = TRUE) 

# Create a vector of labels with the same length as the number of columns in 'countryfacts'
labels <- c("code","country","codeWVS","Homicide","GDP","InfMort","LifeExp","GINI","GenderPEdu","code2")




# Print the result
print(countryfacts)
```

```{r}
# Load the dplyr package if not already loaded
if (!require(dplyr)) {
  install.packages("dplyr")
  library(dplyr)
}

# Create the 'hardship' column in the 'countryfacts' data frame
countryfacts <- countryfacts %>%
  mutate(hardship = (homiciderate + gdp + infantmortality + lifeexpectancy + gini + femalemale_primedu) / 6)
countryfacts



# View the distribution of the 'hardship_index' column for each country
hardship_index_distribution <- countryfacts %>%
  group_by(label) %>%
  summarize(
    mean = mean(hardship, na.rm = TRUE),
    median = median(hardship, na.rm = TRUE),
    sd = sd(hardship, na.rm = TRUE),
    min = min(hardship, na.rm = TRUE),
    max = max(hardship, na.rm = TRUE),
    n = sum(!is.na(hardship))
  )

# Print the result
print(hardship_index_distribution)
```

# table with female percentage, mean age, mean risk taking per countries (summary of the countries)
```{r}

library(dplyr)

table_data <- data %>%
  group_by(country) %>%
  summarise(
    n = n(),
    female_percentage = mean(gender == 1) * 100,
    mean_age = mean(age, na.rm = TRUE),
    age_range = paste(min(age, na.rm = TRUE), "-", max(age, na.rm = TRUE)),
    mean_risktaking = mean(Z_score_risktaking, na.rm = TRUE)
  )

table_data
data





```

#graph across countries: risk taking vs age vs gender (Z-score for age and risk taking)   
```{r}
# Assuming 'data' is your data frame with a column 'age'
data$z_age <- scale(data$age)

ggplot(data, aes(z_age, Z_score_risktaking, color = factor(gender))) +
  geom_point(size = 0.1) +  
  geom_smooth(method = "lm") +
  scale_color_manual(values = c("blue", "red"), labels = c("Male", "Female")) +
  labs(color = "Gender", x = "Age", y = "Risk Taking") +
  theme_minimal()
Model1 <- lm(Z_score_risktaking ~ z_age * factor(gender), data = data)
Model1
```

#regression table (risk taking and age -> Z-score)
```{r}
regression_results <- data %>%
  group_by(country) %>%
  do(model = lm(Z_score_risktaking ~ z_age + gender, data = .)) %>%
  summarize(
    country = first(country),
    intercept = coef(summary(model))[1, 1],
    slope_age = coef(summary(model))[2, 1],
    slope_gender = coef(summary(model))[3, 1]
  )

regression_results

write.csv(regression_results, "/Users/cristinacandido/Documents/Github/risk_wvs/regression_results.csv", row.names = FALSE)
```


```{r}
```






















