---
title: "R Notebook"
output: html_notebook
---
Variables: 

Risk
Age 
Sex
Country



```{r}
library(data.table)
library(tidyr)
```

#read the data (Wave 5)
```{r}
# Data of Wave 5


WV5_data <- readRDS("/Users/cristinacandido/Documents/Github/risk_wvs/data/WVS/F00007944-WV5_Data_R_v20180912.rds")


# Convert WV5_data-object in data.frame 
WV5_data_df <- as.data.frame(WV5_data)

# show first five columns
head(WV5_data_df[, 1:5])
```

# clean the data set
```{r}
library(dplyr)

#rename the variables
WV5_data <- WV5_data_df %>%
  rename(sex = V235, age = V237, country = V2, wave = V1, risk = V86)
WV5_data


#select only the variables of interest
WV5_data <- WV5_data %>%
  select(sex, age, country, wave, risk)
WV5_data
```

```{r}
#decode the country names 
countrynames = read.csv("/Users/cristinacandido/Documents/Github/risk_wvs/data/WVS/countrynames.txt", header=FALSE,as.is=TRUE)
colnames(countrynames) = c("code", "name")
WV5_data$country_lab = countrynames$name [match(WV5_data$country, countrynames$code)]
table(WV5_data$country_lab)
WV5_data


```

#Read Dataset (Wave 6)
```{r}
WV6_data <- load("/Users/cristinacandido/Documents/Github/risk_wvs/data/WVS/WV6_Data_R_v20201117.rdata") 
WV6_data <- WV6_Data_R_v20201117 
print(WV6_data)
```

#rename variables
```{r}
WV6_data <- WV6_data %>%
  rename(wave = V1, sex = V240, age = V242,country = V2, risk = V76)


#select only the variables of interest
WV6_data <- WV6_data %>%
  select(wave, sex, age, country, sex,risk)
WV6_data

```


#decode daraset (Wave 6)
```{r}
countrynames = read.csv("/Users/cristinacandido/Documents/Github/risk_wvs/data/WVS/countrynames.txt", header=FALSE,as.is=TRUE)
colnames(countrynames) = c("code", "name")
WV6_data$country_lab = countrynames$name [match(WV6_data$country, countrynames$code)]
table(WV6_data$country_lab)
WV6_data
```

#combine the 2 dataset (Wave 6 + Wave 5)
```{r}
WV5_data
WV6_data
data = rbind(WV5_data, WV6_data)
data

#number of countries

length(unique(data$country_lab))
```
#exclusion of participants and omission of missing data (na)
```{r}
data = subset(data, risk > 0 & sex > 0 & age >0 )
data_Wave5 = subset(WV5_data, risk > 0 & sex > 0 & age >0 )
data_Wave6 = subset(WV6_data, risk > 0 & sex > 0 & age >0)
data <- na.omit(data)
data_Wave5 <- na.omit(data_Wave5)
data_Wave6 <- na.omit(data_Wave6)



#number of participants per Wave

nrow(data)
nrow(data_Wave5)
nrow(data_Wave6)
```
```{r}
# Load the dplyr package
library(dplyr)

# Assuming the data frame is called 'data' and the column containing the country information is called 'country'
country_counts <- data %>%
  count(country_lab)

# Print the result
print(country_counts)

```

#number and list and participants pro countries pro Wave (including both Waves together)
```{r}
table(data_Wave5$country_lab)
length(unique(data_Wave5$country_lab)) 
table(data_Wave6$country_lab)
length(unique(data_Wave6$country_lab))
length(unique(data$country_lab)) 
table(data$country_lab)
```


```{r}
data$risk = 6 - data$risk + 1
data$risk_ord=data$risk 
data$risk = 10*scale(data$risk, center=TRUE,scale=TRUE)+50
data


```

#number of males vs females (1 = males; 2 = females)
```{r}
table(data$sex)
table(data_Wave5$sex)
table(data_Wave6$sex)
```


```{r}
#create a categorical age variable
data$agecat[data$age<20]="15-19"
data$agecat[data$age>=20 & data$age <30] = "20-29"
data$agecat[data$age>=30 & data$age <40] = "30-39"
data$agecat[data$age>=40 & data$age <50] = "40-49"
data$agecat[data$age>=50 & data$age <60] = "50-59"
data$agecat[data$age>=60 & data$age <70] = "60-69"
data$agecat[data$age>=70 & data$age <80] = "70-79"
data$agecat[data$age>=80] = "80+"
```


#gender variables
```{r}
data$sex[data$sex == 1] <- "male"
data$sex[data$sex == 2] <- "female"

data_Wave5$sex[data_Wave5$sex == 1] <- "male"
data_Wave5$sex[data_Wave5$sex == 2] <- "female"

data_Wave6$sex[data_Wave6$sex == 1] <- "male"
data_Wave6$sex[data_Wave6$sex == 2] <- "female"

#average age of participants
mean(data$age)
median(data$age)
```

#wave variables
```{r}
data$wave[data$wave == 5] <- "Wave 5"
data$wave[data$wave == 6] <- "Wave 6"
data
```


#age range
```{r}
range(data$age) 
range(data_Wave5$age)
range(data_Wave6$age)
```
#risk taking Frequency
```{r}
library(ggplot2)
ggplot(data, aes(x = risk)) +
  geom_histogram(binwidth = 0.5, fill = "lightblue", color = "black") +
  labs(x = "Risk Taking", y = "Frequency", title = "Histogram of Risk Taking") +
  theme_minimal()
```
#age frequency
```{r}
ggplot(data, aes(x = age)) +
  geom_histogram(binwidth = 0.5, fill = "lightblue", color = "black") +
  labs(x = "Age", y = "Frequency", title = "Histogram of Age Distributionn") +
  theme_minimal()
```
#age vs risk taking
```{r}

ggplot(data, aes(x = agecat, y = risk)) +
  geom_boxplot() +
  labs(title = "Boxplot of Risk and Adventure by Age",
       x = "Age",
       y = "Risk and Adventure") +
  theme_minimal()


```
#sex vs risk taking
```{r}
ggplot(data, aes(as.factor(sex), risk))+
  geom_boxplot()

```
```{r}
#descriptive data 
summary(data)
```
```{r}
#data cleaning: deletion of NAs 
data = na.omit(data)
summary(data)
```
```{r}
#risk distribution according to Waves 5 and 6 
ggplot(data, aes(as.factor(wave), risk))+
  geom_boxplot()
```
```{r}
#risk vs age
library(ggplot2)
ggplot(data, aes(risk, age))+
  geom_point()+
  geom_smooth(method = "lm")
```


```{r}
#selected 3 countries: Andorra, Romania, Spain
data1 <- subset(data, country_lab %in% c("Andorra", "Romania", "Spain"))
# 3 risk distribution for 3 countries
ggplot(data1, aes(as.factor(country_lab), risk))+
  geom_boxplot()
```
```{r}
#age vs risk depending on country
ggplot(data, aes(age, risk, color = as.factor(country_lab)))+
  geom_point()+
  geom_smooth(method = "lm", se = TRUE)
```
```{r}
```

```{r}
# read in file that contains hardship indicators manually collected from CIA factbook, WHO, and World Bank 
# (see Supplemental Materials for URL sources)
countryfacts = read.csv("/Users/cristinacandido/Documents/Github/risk_wvs/data/WVS/countryfacts_selection.csv", as.is = TRUE, header = TRUE) 

# Create a vector of labels with the same length as the number of columns in 'countryfacts'
labels <- c("code","country","codeWVS","Homicide","GDP","InfMort","LifeExp","GINI","GenderPEdu","code2")




# Print the result
print(countryfacts)
```

```{r}
# Load the dplyr package
library(dplyr)

# Assuming the data frame is called 'data' and the column containing the country information is called 'country'
age_counts <- data %>%
  count(agecat)

# Print the result
print(age_counts)
```
```{r}
summary(data)
```


```{r}

# Load the dplyr package
library(dplyr)

# Create age categories
data <- data %>%
  mutate(agecat = cut(age, breaks = c(0, 18, 35, 50, 65, 100), 
                      labels = c('0-18', '19-35', '36-50', '51-65', '66+')))

# Count the number of occurrences of each age category for each country
agepercountries_counts <- data %>%
  group_by(country_lab) %>%
  count(agecat)

# Print the result
print(agepercountries_counts)

```

```{r}
# Load the dplyr package if not already loaded
if (!require(dplyr)) {
  install.packages("dplyr")
  library(dplyr)
}

# Count the number of occurrences of each gender for each country
sexpercountries_counts <- data %>%
  group_by(country_lab) %>%
  count(sex)

# Print the result
print(sexpercountries_counts)

```
```{r}
# Load the dplyr package if not already loaded
if (!require(dplyr)) {
  install.packages("dplyr")
  library(dplyr)
}

# Group the data by country and calculate the age distribution
age_distribution_per_country <- data %>%
  group_by(country_lab) %>%
  summarize(mean_age = mean(age, na.rm = TRUE),
            median_age = median(age, na.rm = TRUE),
            min_age = min(age, na.rm = TRUE),
            max_age = max(age, na.rm = TRUE))

# Print the result
print(age_distribution_per_country)

```

```
```










