---
title: "01_GPS_WVS"
output: html_document
date: "2024-05-08"
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, results = 'hide', message = FALSE, warning = FALSE)
rm(list = ls())
```

# Set path Laura: ONLY USE FOR LAURA 
```{r}
# base_path <- "//home.kt.ktzh.ch/B117T23$/Desktop/Riskktaking/Data"
base_path <- "/Users/laurabazzigher/Documents/GitHub/risk_wvs/data/dataset/Data_S3"
```

# Library 
```{r}
library(data.table)
library(tidyr)
library(maps)
library(haven)
library(ggplot2)
library(dplyr)
library(readxl)
library(lmerTest)
library(lme4)
library(broom)
library(tibble)
library(readr)
```


# Data
## Load data 
```{r}
# Countryfacts
countryfacts <- read_excel(file.path(base_path, "Hardship_complete_2024_Extended.xlsx"))

# Data GPS 
gps_data <- haven::read_dta(file.path(base_path, "individual_new.dta"))

# Data of Wave 5
WV5_data <- readRDS(file.path(base_path, "F00007944-WV5_Data_R_v20180912.rds"))
WV5_data_df <- as_tibble(WV5_data) # Convert WV5_data-object to tibble

# Data of wave 6
load(file.path(base_path, "WV6_Data_R_v20201117.rdata")) 
WV6_data <- as_tibble(WV6_Data_R_v20201117) # Convert WV6_data-object to tibble

# countrynames (to decode the dataset 5/6)
countrynames <- read_csv(file.path(base_path, "countrynames.txt"), col_names = FALSE) %>%
  rename(code = X1, name = X2) # Rename columns for better readability
```

# COUNTRYFACTS 
## check countryfacts 
```{r}
# Plot histograms for each numeric variable
countryfacts %>% 
  select_if(is.numeric) %>% 
  gather() %>% 
  ggplot(aes(value)) + 
  facet_wrap(~key, scales = "free") + 
  geom_histogram(bins = 30) + 
  theme_minimal()

# Check the correlation matrix
cor_matrix <- cor(countryfacts %>% select_if(is.numeric), use = "complete.obs")
print(cor_matrix)
```


## Log Countryfacts 
```{r}
# Log-transform the variables using dplyr
countryfacts <- countryfacts %>%
  mutate(
    homiciderate = log(homiciderate),
    gdp = log(gdp),
    infantmortality = log(infantmortality),
    lifeexpectancy = log(lifeexpectancy),
    alcusedis = log(alcusedis),
    anxietydis= log(anxietydis),
    adhd = log(adhd),
    autism= log(autism),
    bipolardis= log(bipolardis),
    conductdis= log(conductdis),
    depressdis= log(depressdis),
    drugusedis= log(drugusedis),
    eatingdis= log(eatingdis),
    hiv_aids_sextrasinf= log(hiv_aids_sextrasinf),
    ediopathicdevintdis= log(ediopathicdevintdis),
    mentaldis= log(mentaldis),
    Othermentaldis= log(Othermentaldis),
    schizophrenia= log(schizophrenia),
    femalemale_primedu = log(femalemale_primedu) 
  )

# View the transformed data
countryfacts

# Plot histograms for each numeric variable
countryfacts %>% 
  select_if(is.numeric) %>% 
  gather() %>% 
  ggplot(aes(value)) + 
  facet_wrap(~key, scales = "free") + 
  geom_histogram(bins = 30) + 
  theme_minimal()
```


## Reverse Coding - Standardize and create hardship_index using dplyr
```{r}
countryfacts <- countryfacts %>%
  mutate(
    homiciderate = scale(homiciderate),
    gdp = scale(-gdp), # reverse coding 
    infantmortality = scale(infantmortality),
    lifeexpectancy = scale(-lifeexpectancy), # reverse coding
    gini = scale(gini),
    femalemale_primedu = scale(-femalemale_primedu), # reverse coding
    alcusedis = scale(alcusedis), # already log-transformed
    anxietydis = scale(anxietydis), # already log-transformed
    adhd = scale(adhd), # already log-transformed
    autism = scale(autism), # already log-transformed
    bipolardis = scale(bipolardis), # already log-transformed
    conductdis = scale(conductdis), # already log-transformed
    depressdis = scale(depressdis), # already log-transformed
    drugusedis = scale(drugusedis), # already log-transformed
    eatingdis = scale(eatingdis), # already log-transformed
    hiv_aids_sextrasinf = scale(hiv_aids_sextrasinf), # already log-transformed
    idiopathicdevintdis = scale(ediopathicdevintdis), # corrected typo
    mentaldis = scale(mentaldis), # already log-transformed
    othermentaldis = scale(Othermentaldis), # corrected typo and already log-transformed
    schizophrenia = scale(schizophrenia), # already log-transformed

    hardship_index = (homiciderate + gdp + gini + lifeexpectancy + infantmortality + 
                      femalemale_primedu + alcusedis + anxietydis + adhd + autism + 
                      bipolardis + conductdis + depressdis + drugusedis + eatingdis + 
                      hiv_aids_sextrasinf + idiopathicdevintdis + mentaldis + 
                      othermentaldis + schizophrenia) / 20
  )

countryfacts
```

## Impute missing values in the hardship indicators using the median
```{r}
countryfacts <- countryfacts %>%
  mutate(across(c("homiciderate", "gdp", "infantmortality", "lifeexpectancy", "gini", "femalemale_primedu", 
                  "alcusedis", "anxietydis", "adhd", "autism", "bipolardis", "conductdis", 
                  "depressdis", "drugusedis", "eatingdis", "hiv_aids_sextrasinf", "ediopathicdevintdis", 
                  "mentaldis", "Othermentaldis", "schizophrenia"),
                ~ifelse(is.na(.), median(., na.rm = TRUE), .)))

countryfacts

# Use the mutate function to change the country name
countryfacts <- countryfacts %>%
  mutate(country = ifelse(label == "Serbia and Montenegro", "Serbia", label))
countryfacts
```

# GPS
## Clean GPS data by removing records with missing values
```{r}
gps_data <- gps_data %>%
  drop_na(country, isocode, risktaking, gender, age)
gps_data
```


## Select only the variables of interest
```{r}
gps_data <- gps_data %>%
  dplyr::select(country, isocode, ison, risktaking, gender, age)
gps_data
```


## Transform risk variable into T-score (mean = 50, sd = 10)
```{r}
gps_data <- gps_data %>%
  mutate(risktaking = 10 * scale(risktaking, center = TRUE, scale = TRUE) + 50)
gps_data
```

## Factor gender and scale age 
```{r}
gps_data <- gps_data %>%
  mutate(
    gender = factor(gender),
    age_scale = scale(age)
  )

gps_data
```

## Bind counrtyfacts and GPS data
```{r}
gps_data <- gps_data %>%
  left_join(countryfacts, by = "country")
head(gps_data)
str(gps_data)

country_counts <- gps_data %>%
  count(country)

# Print the result
print(country_counts)
```

# WVS
## Data wave 5
## rename and select variables of interest
```{r}
data5 <- WV5_data_df %>%
  rename(gender = V235, age = V237, country_code = V2, wave = V1, risktaking = V86, children = V56, married = V55, employed = V241, education = V238)

#select only the variables of interest
data5 <- data5 %>%
  dplyr::select(gender, age, country_code, wave, risktaking, children, married, employed, education)
data5

# Assuming WV5_data has a column named country_code
data5$country <- countrynames$name[match(data5$country_code, countrynames$code)]

# Check the frequency of each country in the new column
table(data5$country)

# Display the updated WV5_data
head(data5)
unique(data5$country)

print(countrynames)

country_counts <- data5 %>%
  count(country)

# Print the result
print(country_counts)
```

## Data wave 6
## rename and select variables of interest
```{r}
data6 <- WV6_data %>%
  rename(wave = V1, gender = V240, age = V242,country_code = V2, risktaking = V76, children = V58, married = V57, employed = V229, education = V248)

# select only the variables of interest
data6 <- data6 %>%
  dplyr::select(wave, gender, age, country_code,risktaking, children, married, employed, education)
data6

data6$country = countrynames$name[match(data6$country_code, countrynames$code)]
table(data6$country)
```

## Bind data5 and data6 
```{r}
wvs_data = rbind(data5, data6)
data

country_counts <- wvs_data %>%
  count(country)

# Print the result
print(country_counts)
```


## Remove missing variables and rename countries
```{r}
wvs_data = subset(wvs_data, risktaking > 0 & gender > 0 & age >0 & education > 0 & employed > 0 & married > 0 & children >= 0)
wvs_data <- na.omit(wvs_data)

wvs_data

# Use the mutate function to change the country name
wvs_data <- wvs_data %>%
  mutate(country = ifelse(country == "Great Britain", "United Kingdom",
                   ifelse(country == "Viet Nam", "Vietnam", country)))

country_counts <- wvs_data %>%
  count(country)

print(country_counts)
```


## Transfrom risk item 
```{r}
# Transform risk item such that high values represent more risk taking
wvs_data <- wvs_data %>%
  mutate(risktaking = 6 - risktaking + 1)

  
# Transform risk variable into T-score (mean = 50, sd = 10)
wvs_data <- wvs_data %>%
  mutate(risktaking = 10 * scale(risktaking, center = TRUE, scale = TRUE) + 50)

#Transform risk variable into Z score 

# Factor gender
wvs_data <- wvs_data %>%
  mutate(gender = factor(gender))

# Make a duplicate of the 'age' variable and scale it
wvs_data <- wvs_data %>%
  mutate(age_scale = scale(age))

# Count the occurrences of each country
country_counts <- wvs_data %>%
  count(country)

# Print the result
print(country_counts)

# Display the updated data
head(wvs_data)
```

## Dichotomizing variables 
```{r}
library(dplyr)

# Transformations für die Variablen
wvs_data <- wvs_data %>%
  mutate(
    gender = if_else(gender == 1, 0, 1), # sex: male vs. female
    children = if_else(children == 0, 0, 1), # children: no vs. yes
    married = if_else(married == 1, 1, 0), # married: yes vs. no
    employed = if_else(employed < 4, 1, 0), # employed: yes vs. no
    education = if_else(education < 4, 0, 1) # education: no primary vs. primary+
  )

# Selektion der Variablen in countryfacts
countryfacts <- countryfacts %>%
  select(label, code, hardship_index)

# Anzeigen der Daten
print(wvs_data)
print(countryfacts)
```

## Create dataset for mixed-models 
```{r}
countryfacts<- rename(countryfacts, country = label)

countryfacts

WVS_data <- left_join(wvs_data, countryfacts, by = "country")
WVS_data

unique(WVS_data$country)
str(WVS_data)
```

```{r}
country_counts <- WVS_data %>%
  count(country)

# Print the result
print(country_counts)
```

# write cvs
## write csv countryfacts
```{r}
write.csv(countryfacts, file = file.path(base_path, "countryfacts_cleaned.csv"), row.names = FALSE)
```

## write csv gps_data
```{r}
write.csv(gps_data, file = file.path(base_path, "gps_cleaned.csv"), row.names = FALSE)
```
## write csv
```{r}
write.csv(WVS_data, file = file.path(base_path, "wvs_cleaned.csv"), row.names = FALSE)
```






