---
title: "4_Hardship_specification_curve_v2"
output: html_document
date: "2024-05-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, results = 'hide', message = FALSE, warning = FALSE)
rm(list = ls())
```

# Set path Laura: ONLY USE FOR LAURA 
```{r}
base_path <- "//home.kt.ktzh.ch/B117T23$/Desktop/Riskktaking/Data"
# base_path <- "/Users/laurabazzigher/Documents/GitHub/risk_wvs/data/dataset/Data_S3"
```

# Library 
```{r}
library(tidyverse)
library(ggplot2)
library(specr)
remotes::install_github("masurp/specr")
library(specr)
library(readxl)
library(ggthemes)
library(cowplot)
library(dplyr)
```

# Load all data
```{r}
# Countryfacts
countryfacts <- read.csv(file.path(base_path, "countryfacts_cleaned.csv"))
str(countryfacts)

risktaking <- read.csv(file.path(base_path, "gps_wvs_combined"), header=TRUE, as.is=TRUE)
str(risktaking)
```


```{r}
risktaking <- merge(countryfacts, risktaking, by = "country")
str(risktaking)
```

# Remove duplicated columns and unnecessary columns
```{r}
risktaking <- risktaking %>%
  select(-ends_with(".y")) %>%
  rename_with(~ gsub("\\.x", "", .), ends_with(".x"))

risktaking <- risktaking %>%
  select(-label, -codeWVS, -worldmap)
str(risktaking)
```
# Calculate correlation with risktaking
```{r}
# Select only the numeric variables, including "risktaking"
numeric_vars <- risktaking %>%
  select_if(is.numeric)

# Calculate the correlations between "risktaking" and all other numeric variables
cor_matrix <- cor(numeric_vars, use = "complete.obs")

# Extract only the correlations that relate to "risktaking"
risktaking_correlations <- cor_matrix["risktaking", ]

# Display the correlations
print(risktaking_correlations)
```

```{r}
# Install and load necessary libraries
library(dplyr)
library(knitr)
library(kableExtra)

# Select only the numeric variables, including "risktaking"
numeric_vars <- risktaking %>%
  select_if(is.numeric)

# Calculate the correlations between "risktaking" and all other numeric variables
cor_matrix <- cor(numeric_vars, use = "complete.obs")

# Extract only the correlations that relate to "risktaking"
risktaking_correlations <- cor_matrix["risktaking", ]

# Create a correlation table
cor_table <- data.frame(
  Variable = names(risktaking_correlations),
  Correlation = round(risktaking_correlations, 5)
)

# You can add other details like P-values, significance, or interpretation if you want to calculate them.

# Display the table using knitr::kable and kableExtra for formatting
cor_table %>%
  kable("html", 
        caption = "Correlations with Risktaking: Summary of Results", 
        col.names = c("Variable", "Correlation"),
        digits = 5,  # Rounding numbers to 3 decimals
        align = "c") %>%  # Center-align columns
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F) %>% 
  column_spec(2, bold = T)  # Make the correlation column bold
```


```{r}
library(Hmisc)

# Select only the numeric variables, including "risktaking"
numeric_vars <- risktaking %>%
  select_if(is.numeric)

# Calculate both the correlation matrix and the p-values using rcorr()
cor_results <- rcorr(as.matrix(numeric_vars))

# Extract the correlation matrix and p-values for 'risktaking'
correlations <- cor_results$r["risktaking", ]  # Correlation values
p_values <- cor_results$P["risktaking", ]      # P-values

# Create a data frame with correlation values, p-values, and significance
cor_table <- data.frame(
  Variable = names(correlations),
  Correlation = round(correlations, 5),
  P_value = format(p_values, scientific = TRUE),  # Display small p-values in scientific notation
  Significant = ifelse(p_values < 0.05, "Yes", "No")  # Flag significant results
)

# Display the table using knitr::kable and kableExtra for formatting
cor_table %>%
  kable("html", 
        caption = "Correlations with Risktaking: Summary of Results", 
        col.names = c("Variable", "Correlation", "P-value", "Significant"),
        digits = 5,  # Rounding numbers to 5 decimals
        align = "c") %>%  # Center-align columns
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F) %>% 
  column_spec(2, bold = T) %>%  # Make the correlation column bold
  column_spec(3, background = "lightyellow")  # Highlight P-value column
```

# Setup for specifications
```{r}
# Setup for specifications
specification <- setup(
  data = risktaking, 
  y = "risktaking",     # dependent variable
  x = c("homiciderate", "gdp", "infantmortality", "lifeexpectancy", "gini", 
        "femalemale_primedu", "alcusedis", "anxietydis", "adhd", "autism", 
        "bipolardis", "conductdis", "depressdis", "drugusedis", "eatingdis", 
        "hiv_aids_sextrasinf", "ediopathicdevintdis", "mentaldis", 
        "Othermentaldis", "schizophrenia"),  
  model = "lm"
)

summary(specification)
```
# run specifications
```{r}
specification_results <- specr(specification)
specification_results

summary(specification_results, digits = 5)
```

# summarizing the parameter distribution
```{r}
summary(specification_results, type = "curve")

summary(specification_results, 
        type = "curve", 
        group = "x",           
        stats = c("median", "mean", "min", "max"))  # Statistiken in einem Vektor auflisten
```

# Plots
```{r}
plot(specification_results)

(a <- plot(specification_results, type = "curve", ci = F, ribbon = T) + 
   geom_point(size = 4))


(b <- plot(specification_results, type = "choices", choices = c("x", "y", "model", "controls")) +
   geom_point(size = 2, shape = 4)) 

(c <- plot(specification_results, type = "samplesizes") + ylim(0, 400))


plot_grid(a, b, c, ncol = 1,
          align = "v",
          rel_heights = c(1.5, 2, 0.8),
          axis = "rbl")

plot(specification_results, type = "boxplot") + 
  geom_point(alpha = .4) + 
  scale_fill_brewer(palette = "Pastel2") +
  labs(x = "Effect size", fill = "")
```

# Subsetting data for males 
```{r}
specification_males <- setup(
  data = risktaking %>%
           filter(gender == 1),  # Filter for males
  y = "risktaking",
  x = c("homiciderate", "gdp", "infantmortality", "lifeexpectancy", "gini", 
        "femalemale_primedu", "alcusedis", "anxietydis", "adhd", "autism", 
        "bipolardis", "conductdis", "depressdis", "drugusedis", "eatingdis", 
        "hiv_aids_sextrasinf", "ediopathicdevintdis", "mentaldis", 
        "Othermentaldis", "schizophrenia"),
  model = "lm"
)

# Run the specifications for males
specification_results_males <- specr(specification_males)

# View the summary of the results
summary(specification_results_males)
```

# Plots for male subset results
```{r}
plot(specification_results_males)

(a_male <- plot(specification_results_males, type = "curve", ci = F, ribbon = T) + 
   geom_point(size = 4))


(b_male <- plot(specification_results_males, type = "choices", choices = c("x", "y", "model", "controls")) +
   geom_point(size = 2, shape = 4)) 

(c_male <- plot(specification_results_males, type = "samplesizes") + ylim(0, 400))


plot_grid(a_male, b_male, c_male, ncol = 1,
          align = "v",
          rel_heights = c(1.5, 2, 0.8),
          axis = "rbl")

plot(specification_results_males, type = "boxplot") + 
  geom_point(alpha = .4) + 
  scale_fill_brewer(palette = "Pastel2") +
  labs(x = "Effect size", fill = "")
```


# Subsetting data for females 
```{r}
specification_females <- setup(
  data = risktaking %>%
           filter(gender == 0),  # Filter for females
  y = "risktaking",
  x = c("homiciderate", "gdp", "infantmortality", "lifeexpectancy", "gini", 
        "femalemale_primedu", "alcusedis", "anxietydis", "adhd", "autism", 
        "bipolardis", "conductdis", "depressdis", "drugusedis", "eatingdis", 
        "hiv_aids_sextrasinf", "ediopathicdevintdis", "mentaldis", 
        "Othermentaldis", "schizophrenia"),
  model = "lm"
)

# Run the specifications for females
specification_results_females <- specr(specification_females)

# View the summary of the results
summary(specification_results_females)
```

# Plots for female subset results
```{r}
plot(specification_results_females)

(a_female <- plot(specification_results_females, type = "curve", ci = F, ribbon = T) + 
   geom_point(size = 4))


(b_female <- plot(specification_results_females, type = "choices", choices = c("x", "y", "model", "controls")) +
   geom_point(size = 2, shape = 4)) 

(c_female <- plot(specification_results_females, type = "samplesizes") + ylim(0, 400))


plot_grid(a_female, b_female, c_female, ncol = 1,
          align = "v",
          rel_heights = c(1.5, 2, 0.8),
          axis = "rbl")

plot(specification_results_females, type = "boxplot") + 
  geom_point(alpha = .4) + 
  scale_fill_brewer(palette = "Pastel2") +
  labs(x = "Effect size", fill = "")
```
