---
title: "S2_GPS"
output: html_document

date: "2024-05-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, results = 'hide', message = FALSE, warning = FALSE)
rm(list = ls())
```

# Set path Laura: ONLY USE FOR LAURA 
```{r}
base_path <- "//home.kt.ktzh.ch/B117T23$/Desktop/Riskktaking/Data"
```

# Library 
```{r}
library(data.table)
library(tidyr)
library(maps)
library(haven)
library(ggplot2)
library(dplyr)
library(readxl)
library(lmerTest)
library(lme4)
library(broom)
library(tibble)
```


# Data
## Load data 
```{r}
# Countryfacts
countryfacts <- read_excel(file.path(base_path, "Hardship_complete_2024.xlsx"))

# Data GPS 
gps_data <- haven::read_dta(file.path(base_path, "individual_new.dta"))

head(gps_data)
```


# COUNTRYFACTS 
## check countryfacts 
```{r}
# Plot histograms for each numeric variable
countryfacts %>% 
  select_if(is.numeric) %>% 
  gather() %>% 
  ggplot(aes(value)) + 
  facet_wrap(~key, scales = "free") + 
  geom_histogram(bins = 30) + 
  theme_minimal()

# Check the correlation matrix
cor_matrix <- cor(countryfacts %>% select_if(is.numeric), use = "complete.obs")
print(cor_matrix)
```


## Log Countryfacts 
```{r}
# Log-transform the variables using dplyr
countryfacts <- countryfacts %>%
  mutate(
    homiciderate = log(homiciderate),
    gdp = log(gdp),
    infantmortality = log(infantmortality),
    lifeexpectancy = log(lifeexpectancy),
    femalemale_primedu = log(femalemale_primedu) # new - not in the original code
  )

# View the transformed data
countryfacts

# Plot histograms for each numeric variable
countryfacts %>% 
  select_if(is.numeric) %>% 
  gather() %>% 
  ggplot(aes(value)) + 
  facet_wrap(~key, scales = "free") + 
  geom_histogram(bins = 30) + 
  theme_minimal()
```

## Reverse Coding - Standardize and create hardship_index using dplyr
```{r}
countryfacts <- countryfacts %>%
  mutate(
    homiciderate = scale(homiciderate),
    gdp = scale(-gdp),
    infantmortality = scale(infantmortality),
    lifeexpectancy = scale(-lifeexpectancy),
    gini = scale(gini),
    femalemale_primedu = scale(-femalemale_primedu),
    hardship_index = (homiciderate + gdp + gini + lifeexpectancy + infantmortality + femalemale_primedu) / 6
  )

countryfacts
```

## Impute missing values in the hardship indicators using the median
```{r}
countryfacts <- countryfacts %>%
  mutate(across(c("homiciderate", "gdp", "infantmortality", "lifeexpectancy", "gini", "femalemale_primedu"),
                ~ifelse(is.na(.), median(., na.rm = TRUE), .)))

countryfacts

# Use the mutate function to change the country name
countryfacts <- countryfacts %>%
  mutate(country = ifelse(label == "Serbia and Montenegro", "Serbia", label))
countryfacts
```

# GPS
## Clean GPS data by removing records with missing values
```{r}
gps_data <- gps_data %>%
  drop_na(country, isocode, risktaking, gender, age)
gps_data
```


## Select only the variables of interest
```{r}
gps_data <- gps_data %>%
  dplyr::select(country, isocode, ison, risktaking, gender, age)
gps_data
```


## Transform risk variable into T-score (mean = 50, sd = 10)
```{r}
gps_data <- gps_data %>%
  mutate(risktaking = 10 * scale(risktaking, center = TRUE, scale = TRUE) + 50)
gps_data
```

## Factor gender and scale age 
```{r}
gps_data <- gps_data %>%
  mutate(
    gender = factor(gender),
    age_scale = scale(age)
  )

gps_data
```

## Bind counrtyfacts and GPS data
```{r}
gps_data <- gps_data %>%
  left_join(countryfacts, by = "country")
head(gps_data)
str(gps_data)
```

# write csv gps_data
```{r}
write.csv(gps_data, file = file.path(base_path, "gps_cleaned.csv"), row.names = FALSE)
```

# write csv countryfacts
```{r}
write.csv(countryfacts, file = file.path(base_path, "countryfacts_cleaned.csv"), row.names = FALSE)
```




