---
title: "S2_WVS"
output: html_document
date: "2024-05-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, results = 'hide', message = FALSE, warning = FALSE)
rm(list = ls())
```

# Set path Laura: ONLY USE FOR LAURA 
```{r}
base_path <- "//home.kt.ktzh.ch/B117T23$/Desktop/Riskktaking/Data"
```

# Library 
```{r}
library(tidyverse)
library(data.table)
library(tidyr)
library(maps)
library(haven)
library(ggplot2)
library(dplyr)
library(readxl)
library(lmerTest)
library(lme4)
library(broom)
library(tibble)
```

# Load all data
```{r}
# Countryfacts
countryfacts <- read_excel(file.path(base_path, "Hardship_complete_2024.xlsx"))

# Data of Wave 5
WV5_data <- readRDS(file.path(base_path, "F00007944-WV5_Data_R_v20180912.rds"))
WV5_data_df <- as_tibble(WV5_data) # Convert WV5_data-object to tibble

# Data of wave 6
load(file.path(base_path, "WV6_Data_R_v20201117.rdata")) 
WV6_data <- as_tibble(WV6_Data_R_v20201117) # Convert WV6_data-object to tibble

# countrynames (to decode the dataset 5)
countrynames <- read_csv(file.path(base_path, "countrynames.txt"), col_names = FALSE) %>%
  rename(code = X1, name = X2) # Rename columns for better readability
```

# COUNTRYFACTS 
## check countryfacts 
```{r}
# Plot histograms for each numeric variable
countryfacts %>% 
  select_if(is.numeric) %>% 
  gather() %>% 
  ggplot(aes(value)) + 
  facet_wrap(~key, scales = "free") + 
  geom_histogram(bins = 30) + 
  theme_minimal()

# Check the correlation matrix
cor_matrix <- cor(countryfacts %>% select_if(is.numeric), use = "complete.obs")
print(cor_matrix)
```

## Log Countryfacts 
```{r}
# Log-transform the variables using dplyr
countryfacts <- countryfacts %>%
  mutate(
    homiciderate = log(homiciderate),
    gdp = log(gdp),
    infantmortality = log(infantmortality),
    lifeexpectancy = log(lifeexpectancy),
    femalemale_primedu = log(femalemale_primedu) # new - not in the original code
  )

# View the transformed data
countryfacts

# Plot histograms for each numeric variable
countryfacts %>% 
  select_if(is.numeric) %>% 
  gather() %>% 
  ggplot(aes(value)) + 
  facet_wrap(~key, scales = "free") + 
  geom_histogram(bins = 30) + 
  theme_minimal()
```

## Reverse Coding - Standardize and create hardship_index using dplyr
```{r}
countryfacts <- countryfacts %>%
  mutate(
    homiciderate = scale(homiciderate),
    gdp = scale(-gdp),
    infantmortality = scale(infantmortality),
    lifeexpectancy = scale(-lifeexpectancy),
    gini = scale(gini),
    femalemale_primedu = scale(-femalemale_primedu),
    hardship_index = (homiciderate + gdp + gini + lifeexpectancy + infantmortality + femalemale_primedu) / 6
  )

countryfacts
```

## Impute missing values in the hardship indicators using the median
```{r}
countryfacts <- countryfacts %>%
  mutate(across(c("homiciderate", "gdp", "infantmortality", "lifeexpectancy", "gini", "femalemale_primedu"),
                ~ifelse(is.na(.), median(., na.rm = TRUE), .)))

countryfacts

# Use the mutate function to change the country name
countryfacts <- countryfacts %>%
  mutate(country = ifelse(label == "Serbia and Montenegro", "Serbia", label))
countryfacts
```


# Data wave 5
## rename and select variables of interest
```{r}
data5 <- WV5_data_df %>%
  rename(gender = V235, age = V237, country_code = V2, wave = V1, risktaking = V86, children = V56, married = V55, employed = V241, education = V238)

#select only the variables of interest
data5 <- data5 %>%
  dplyr::select(gender, age, country_code, wave, risktaking, children, married, employed, education)
data5

# Assuming WV5_data has a column named country_code
data5$country <- countrynames$name[match(data5$country_code, countrynames$code)]

# Check the frequency of each country in the new column
table(data5$country)

# Display the updated WV5_data
head(data5)
unique(data5$country)

print(countrynames)

country_counts <- data5 %>%
  count(country)

# Print the result
print(country_counts)
```

# Data wave 6
## rename and select variables of interest
```{r}
data6 <- WV6_data %>%
  rename(wave = V1, gender = V240, age = V242,country_code = V2, risktaking = V76, children = V58, married = V57, employed = V229, education = V248)

# select only the variables of interest
data6 <- data6 %>%
  dplyr::select(wave, gender, age, country_code,risktaking, children, married, employed, education)
data6

data6$country = countrynames$name[match(data6$country_code, countrynames$code)]
table(data6$country)
```

# Bind data5 and data6 
```{r}
data = rbind(data5, data6)
data

country_counts <- data %>%
  count(country)

# Print the result
print(country_counts)
```


## Remove missing variables 
```{r}
data = subset(data, risktaking > 0 & gender > 0 & age >0 & education > 0 & employed > 0 & married > 0 & children >= 0)
data <- na.omit(data)

data

# Use the mutate function to change the country name
data <- data %>%
  mutate(country = ifelse(country == "Great Britain", "United Kingdom", country))
```


## Transfrom risk item 
```{r}
# Transform risk item such that high values represent more risk taking
data <- data %>%
  mutate(risktaking = 6 - risktaking + 1)

  
# Transform risk variable into T-score (mean = 50, sd = 10)
data <- data %>%
  mutate(risktaking = 10 * scale(risktaking, center = TRUE, scale = TRUE) + 50)

#Transform risk variable into Z score 

# Factor gender
data <- data %>%
  mutate(gender = factor(gender))

# Make a duplicate of the 'age' variable and scale it
data <- data %>%
  mutate(age_scale = scale(age))

# Count the occurrences of each country
country_counts <- data %>%
  count(country)

# Print the result
print(country_counts)

# Display the updated data
head(data)
```

## Dichotomizing variables 
```{r}
library(dplyr)

# Transformations für die Variablen
data <- data %>%
  mutate(
    gender = if_else(gender == 1, 0, 1), # sex: male vs. female
    children = if_else(children == 0, 0, 1), # children: no vs. yes
    married = if_else(married == 1, 1, 0), # married: yes vs. no
    employed = if_else(employed < 4, 1, 0), # employed: yes vs. no
    education = if_else(education < 4, 0, 1) # education: no primary vs. primary+
  )

# Selektion der Variablen in countryfacts
countryfacts <- countryfacts %>%
  select(label, code, hardship_index)

# Anzeigen der Daten
print(data)
print(countryfacts)
```

## Create dataset for mixed-models 
```{r}
countryfacts<- rename(countryfacts, country = label)

countryfacts

WVS_data <- left_join(data, countryfacts, by = "country")
WVS_data

unique(WVS_data$country)
str(WVS_data)
```

# write csv
```{r}
write.csv(WVS_data, file = file.path(base_path, "wvs_cleaned.csv"), row.names = FALSE)
```






