---
title: "R Notebook"
output: html_notebook
---

#### To Do: 
# 1. Load 
# 2. Key variables
# 3. descriptives --> how many countries, participants 
# 4. How to visualize? do we want to do the visualization? Per Country or all together // coulors? etc. 
# 5. What do we want to present? 
- Presentation 19.12.2023 
- finalise presentation 05.12.2023 with rui
- Send presentation 27.11.2023 
- Presentation content 
  - why we do this 
  - research gap 
  - method 
  - results
  - challenges 
  - conclusion 
  ---> Do the Presentation on GoogleSlides 
- cancel 12.12.2023 und 19.12.2023 

# etc. ..... 

#Install packages 
```{r}
install.packages("haven")
```

#Load packages 
```{r}
library(data.table)
library(tidyr)
library(haven)
library(ggplot2)
```


#Add data GBD
```{r}
# Arbeitsverzeichnis ändern
setwd("/Users/laurabazzigher/Documents/GitHub/risk_wvs/data/dataset/GBD")
```


```{r}
# Store file names in a vector
filenames <- c(
  "IHME-GBD_2019_DATA1.csv",
  "IHME-GBD_2019_DATA2.csv",
  "IHME-GBD_2019_DATA3.csv",
  "IHME-GBD_2019_DATA4.csv"
)

datalist <- list() # Create an empty list to store the data

# Loop to read the files
for (filename in filenames) {
  data <- read.csv(filename)
  datalist[[filename]] <- data
}

# List the names of the imported files
for (i in 1:length(datalist)) {
  cat("Imported file:", filenames[i], "\n")
}

head(datalist[["IHME-GBD_2019_DATA1.csv"]]) # Accessing the first rows of the first file
```

# Combine the data from the four files
```{r}
combined_data <- do.call(rbind, datalist)

first_row <- head(combined_data, n = 1) #display the first row of the combined dataset
```







