---
title: "R Notebook"
output: html_notebook
---

```{r}
library(data.table)
library(tidyr)
library(maps)
library(haven)
library(ggplot2)
library(dplyr)
library(readxl)
library(ggrepel)
library(wordcloud)
```

####################
####################
####################
PREPARATION DATASETS FOR ANALYSIS
####################
####################
####################

####################
PREP THE DATASET FOR ANALYSIS WVS 5 & 6
####################

#read the data (Wave 5)
```{r}
# Data of Wave 5
WV5_data <- readRDS("/Users/laurabazzigher/Documents/GitHub/risk_wvs/data/dataset/WV6_dataset_wave_5_6/F00007944-WV5_Data_R_v20180912.rds")

# Convert WV5_data-object in data.frame 
WV5_data_df <- as.data.frame(WV5_data)

# show first five columns
WV5_data_df
```

# clean the data set
```{r}
#rename the variables
WV5_data <- WV5_data_df %>%
  rename(gender = V235, age = V237, country_code = V2, wave = V1, risktaking = V86, children = V56, married = V55, employed = V241, education = V238)
WV5_data

colnames(WV5_data)

#select only the variables of interest
WV5_data <- WV5_data %>%
  dplyr::select(gender, age, country_code, wave, risktaking, children, employed, education, married)
WV5_data
```
# Read countrynames data from the CSV file (to decode the dataset 5)
```{r}
countrynames <- read.csv("/Users/laurabazzigher/Documents/GitHub/risk_wvs/data/dataset/WV6_dataset_wave_5_6/countrynames.txt", header = FALSE, as.is = TRUE)
colnames(countrynames) <- c("code", "name")

# Assuming WV5_data has a column named country_code
WV5_data$country <- countrynames$name[match(WV5_data$country_code, countrynames$code)]

# Check the frequency of each country in the new column
table(WV5_data$country)

# Display the updated WV5_data
print(WV5_data)
```

#Read Dataset (Wave 6)
```{r}
WV6_data <- load("/Users/laurabazzigher/Documents/GitHub/risk_wvs/data/dataset/WV6_dataset_wave_5_6/WV6_Data_R_v20201117.rdata") 
WV6_data <- WV6_Data_R_v20201117 
print(WV6_data)
```

#rename variables
```{r}
WV6_data <- WV6_data %>%
  rename(wave = V1, gender = V240, age = V242,country_code = V2, risktaking = V76, children = V58, married = V57, employed = V229, education = V248)

#select only the variables of interest
WV6_data <- WV6_data %>%
  dplyr::select(gender, age, country_code, wave, risktaking, children, employed, education, married)
WV6_data
```

#decode daraset (Wave 6)
```{r}
countrynames = read.csv("/Users/laurabazzigher/Documents/GitHub/risk_wvs/data/dataset/WV6_dataset_wave_5_6/countrynames.txt", header=FALSE,as.is=TRUE)
colnames(countrynames) = c("code", "name")
WV6_data$country = countrynames$name [match(WV6_data$country_code, countrynames$code)]
table(WV6_data$country)
WV6_data
```

#combine the 2 dataset (Wave 6 + Wave 5)
```{r}
WV5_data
WV6_data
WVS_data = rbind(WV5_data, WV6_data)
WVS_data
```

#exclusion of participants and omission of missing data (na)
```{r}
WVS_data = subset(WVS_data, risktaking > 0 & gender > 0 & age >0 & education > 0 & employed > 0 & married > 0 & children >= 0)
data_Wave5 = subset(WV5_data, risktaking > 0 & gender > 0 & age >0 & education > 0 & employed > 0 & married > 0 & children >= 0)
data_Wave6 = subset(WV6_data, risktaking > 0 & gender > 0 & age >0 & education > 0 & employed > 0 & married > 0 & children >= 0)
WVS_data <- na.omit(WVS_data)
data_Wave5 <- na.omit(data_Wave5)
data_Wave6 <- na.omit(data_Wave6)

# Use the mutate function to change the country name
WVS_data <- WVS_data %>%
  mutate(country = ifelse(country == "Great Britain", "United Kingdom", country))
```

#Transformation of item risktaking
```{r}
# Transfrom risk item such that high values represent more risk taking
WVS_data$risktaking = 6 - WVS_data$risktaking + 1

# Transform risk variable into T-score (mean = 50, sd = 10)
WVS_data$T_score_risktaking = 10*scale(WVS_data$risktaking, center=TRUE,scale=TRUE)+50

WVS_data

#Transform risk variable into Z score 
# Assuming T-scores have a mean of 50 and a standard deviation of 10
WVS_data$Z_score_risktaking = (WVS_data$T_score_risktaking - 50) / 10

# Print the resulting data frame
print(WVS_data)

WVS_data <- WVS_data %>%
  group_by(country) %>%
  mutate(z_score_age = scale(age))
WVS_data
```

# Dichotomizing Variables: This helps estimating and interpreting the models later on...
```{r}
WVS_data$gender = ifelse(WVS_data$gender == 1, 0, 1) # sex: male vs. female
WVS_data$children = ifelse(WVS_data$children == 0, 0, 1) # children: no vs. yes
WVS_data$married = ifelse(WVS_data$married == 1, 1, 0) # married: yes vs. no
WVS_data$employed = ifelse(WVS_data$employed < 4, 1, 0) # employed: yes vs. no
WVS_data$education = ifelse(WVS_data$education < 4, 0, 1) # education: no primary vs. primary+ 
```

####################
PREP THE DATASET FOR ANALYSIS GPS
####################

#Add data GPS
```{r}
gps_data <- haven::read_dta("/Users/laurabazzigher/Documents/GitHub/risk_wvs/data/dataset/GPS_dataset_individual_level/individual_new.dta")

head(gps_data)
```

# Clean the data by removing records with missing values
```{r}
gps_data <- gps_data %>%
  drop_na(country, isocode, risktaking, gender, age)

# Display the cleaned data
gps_data
```

#select only the variables of interest
```{r}
gps_data <- gps_data %>%
  dplyr::select(country, isocode, ison, risktaking, gender, age)
gps_data
```
# Transform age (z-score)
```{r}
gps_data <- gps_data %>%
  group_by(country) %>%
  mutate(z_score_age = scale(age))

# Display the new column with Z-Scores per Country
gps_data
```

####################
PREP THE DATASET FOR ANALYSIS HARDSHIP
####################

# read in file that contains hardship indicators manually collected from CIA factbook, WHO, and World Bank 
```{r}
excel_path <- "/Users/laurabazzigher/Documents/GitHub/risk_wvs/data/dataset/Hardship/Hardship_complete_2024.xlsx"
hardship <- read_excel(excel_path)

# Create a vector of labels with the same length as the number of columns in 'countryfacts'
labels <- c("country","mean_homicide","gdp","gini_income","Infant_mortality","life_expect","primary_female_enrollment_rate")

# Print the result
print(hardship)
```


# Create the 'hardship' column in the 'hardship' data frame
```{r}
# Create the 'hardship' column in the 'hardship' data frame
hardship <- hardship %>%
  mutate(hardship = (mean_homicide + gdp + gini_income + Infant_mortality + life_expect + primary_female_enrollment_rate) / 6)
hardship
```
# log transform
```{r}
hardship$mean_homicide=log(hardship$mean_homicide)
hardship$gdp=log(hardship$gdp)
hardship$Infant_mortality=log(hardship$Infant_mortality)
hardship$life_expect=log(hardship$life_expect)
hardship$gini_income=log(hardship$gini_income)
hardship$primary_female_enrollment_rate=log(hardship$primary_female_enrollment_rate)

# changing variables into the same direction

# Reverse Codierung
hardship$mean_homicide=scale(hardship$mean_homicide)
hardship$gdp=scale(-hardship$gdp)
hardship$Infant_mortality=scale(hardship$Infant_mortality)
hardship$life_expect=scale(-hardship$life_expect)
hardship$gini_income=scale(hardship$gini_income)
hardship$primary_female_enrollment_rate=scale(hardship$primary_female_enrollment_rate)

hardship
```

# create a hardship index
```{r}
hardship$hardship=(hardship$mean_homicide+hardship$gdp+hardship$gini_income+hardship$life_expect+hardship$Infant_mortality+hardship$primary_female_enrollment_rate)/6

hardship
```

####################
PREP THE DATASET FOR ANALYSIS MIXED-MODELS
####################

#Add Hardship to WVS_data
```{r}
WVS_mixed_model <- left_join(WVS_data, hardship, by = "country")
WVS_mixed_model
```

#Add Hardship to gps_data
```{r}
gps_mixed_model <- left_join(gps_data, hardship, by = "country")
gps_mixed_model
```

####################
####################
####################
DESCRIPTIVE INFORMATION 
####################
####################
####################

#table with female percentage, mean age, mean risk taking per countries (summary of the countries)
```{r}
table_data_WVS <- WVS_data %>%
  group_by(country) %>%
  summarise(
    n = n(),
    female_percentage = mean(gender == 1) * 100,
    mean_age = mean(age, na.rm = TRUE),
    age_range = paste(min(age, na.rm = TRUE), "-", max(age, na.rm = TRUE)),
    mean_risktaking = mean(Z_score_risktaking, na.rm = TRUE)
  )

table_data_WVS
```

# R code to count observations by country in the WVS_data dataset
```{r}
country_counts <- WVS_data %>%
  count(country)

# Print the result
print(country_counts)
```

# View the distribution of the 'hardship_index' column for each country
```{r}
hardship_index_distribution <- hardship %>%
  group_by(country) %>%
  summarize(
    mean = mean(hardship, na.rm = TRUE),
    median = median(hardship, na.rm = TRUE),
    sd = sd(hardship, na.rm = TRUE),
    min = min(hardship, na.rm = TRUE),
    max = max(hardship, na.rm = TRUE),
    n = sum(!is.na(hardship))
  )

# Print the result
print(hardship_index_distribution)
```

####################
####################
####################
VISUALIZATION 
####################
####################
####################

#World map 
```{r}
world_map <- map_data("world")
recorded_countries <- unique(WVS_data$country)
world_map$recorded <- ifelse(world_map$region %in% recorded_countries, "Recorded", "Not Recorded")

ggplot(world_map, aes(x = long, y = lat, group = group, fill = recorded)) + 
  geom_polygon(color = "white") +
  scale_fill_manual(values = c("Recorded" = "red", "Not Recorded" = "lightgrey"), guide = "none") +
  theme_void() +
  labs(title = "WVS", fill = "Status") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5))
```

#graph across countries: risk taking vs age vs gender (Z-score for age and risk taking)   
```{r}
# Risk vs age with color-coded gender per Country
# Risk vs age with color-coded gender per Country
# Skalierung des Z-Scores für das Alter anpassen
WVS_data$z_score_age_scaled <- 15 * WVS_data$z_score_age + 42


ggplot(WVS_data, aes(z_score_age_scaled, Z_score_risktaking, color = as.factor(gender))) +
  geom_point(position = position_jitter(width = 0.1, height = 0.1), size = 0.1) +  
  geom_smooth(method = "lm") +
  geom_vline(xintercept = 42, linetype = "dashed", color = "black", size = 1) +  
  scale_color_manual(values = c("blue", "red"), labels = c("Male", "Female")) +
  labs(color = "Gender") +
  xlab("Age") +
  ylab("Risk Taking") +
  scale_x_continuous(breaks = seq(0, 100, by = 15), limits = c(0, 100)) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))

WVS_data
```

#regression table (risk taking and age -> Z-score)
```{r}
regression_results_WVS <- WVS_data %>%
  group_by(country) %>%
  do(model = lm(Z_score_risktaking ~ scale(age) + gender, data = .)) %>%
  summarize(
    country = first(country),
    intercept = coef(summary(model))[1, 1],
    slope_age = coef(summary(model))[2, 1],
    slope_gender = coef(summary(model))[3, 1]
  )

regression_results_WVS
```

#table intercept and slope 
```{r}
regression_results_gps <- gps_data %>%
  group_by(country) %>%
  do(model = lm(risktaking ~ z_score_age + gender, data = .)) %>%
  summarize(
    country = first(country),
    intercept = coef(summary(model))[1, 1],
    slope_age = coef(summary(model))[2, 1],
    slope_gender = coef(summary(model))[3, 1]
  )

regression_results_gps
```

# Countries, that are in both datasets
```{r}
common_countries <- intersect(WVS_data$country, gps_data$country)
common_countries
```


# Filtering Selected Countries from dataset gps_data and creating a new set
```{r}
# Countries that are in both datasets
common_countries <- intersect(WVS_data$country, gps_data$country)

# Filter original dataset based on common countries
new_gps <- gps_data[gps_data$country %in% common_countries, ]

# View the new dataset
new_gps
```

# Regression Analysis of Risk-Taking Behavior in New WVS Data
```{r}
regression_results_WVS_new <- new_WVS %>%
  group_by(country) %>%
  do(model = lm(Z_score_risktaking ~ scale(age) + gender, data = .)) %>%
  summarize(
    country = first(country),
    intercept_WVS = coef(summary(model))[1, 1],
    slope_age_WVS = coef(summary(model))[2, 1],
    slope_gender_WVS = coef(summary(model))[3, 1]
  )

regression_results_WVS_new
```

# Regression Analysis of Risk-Taking Behavior in new_gps Data
```{r}
regression_results_gps_new <- new_gps %>%
  group_by(country) %>%
  do(model = lm(risktaking ~ scale(age) + gender, data = .)) %>%
  summarize(
    country = first(country),
    intercept_gps = coef(summary(model))[1, 1],
    slope_age_gps = coef(summary(model))[2, 1],
    slope_gender_gps = coef(summary(model))[3, 1]
  )

regression_results_gps_new
```

#Merging Regression Results with Additional Data and Hardship Index
```{r}
regression_results_gps_new
regression_results_WVS_new

# Assuming "country" is the common column
merged_results <- merge(regression_results_gps_new, regression_results_WVS_new, by = "country", all = TRUE)

# Read data from the Excel file
new_data <- read_excel("/Users/laurabazzigher/Documents/GitHub/risk_wvs/data/dataset/Hardship/Hardship_complete_2024.xlsx")

# Now you can work with the 'new_data' object
print(new_data)

# Perform the left_join operation
new_data <- left_join(merged_results, new_data, by = "country")

# Select specific columns
new_data <- new_data %>%
  dplyr::select(country, intercept_gps, slope_age_gps, slope_gender_gps, intercept_WVS, slope_age_WVS, slope_gender_WVS, isocode)

# Print the final data
print(new_data)

hardship_index <- read_excel("/Users/laurabazzigher/Documents/GitHub/risk_wvs/data/dataset/Hardship/Hardship_complete_2024.xlsx")
print(hardship_index)

hardship_data_complete <- left_join(regression_results_WVS, hardship_index, by = "country")
hardship_data_complete
```


# log transform
```{r}
hardship_data_complete$mean_homicide=log(hardship_data_complete$mean_homicide)
hardship_data_complete$gdp=log(hardship_data_complete$gdp)
hardship_data_complete$Infant_mortality=log(hardship_data_complete$Infant_mortality)
hardship_data_complete$life_expect=log(hardship_data_complete$life_expect)
hardship_data_complete$gini_income=log(hardship_data_complete$gini_income)
hardship_data_complete$primary_female_enrollment_rate=log(hardship_data_complete$primary_female_enrollment_rate)

# changing variables into the same direction

# Reverse Codierung
hardship_data_complete$mean_homicide=scale(hardship_data_complete$mean_homicide)
hardship_data_complete$gdp=scale(-hardship_data_complete$gdp)
hardship_data_complete$Infant_mortality=scale(hardship_data_complete$Infant_mortality)
hardship_data_complete$life_expect=scale(-hardship_data_complete$life_expect)
hardship_data_complete$gini_income=scale(hardship_data_complete$gini_income)
hardship_data_complete$primary_female_enrollment_rate=scale(hardship_data_complete$primary_female_enrollment_rate)

hardship_data_complete
```

# create a hardship index
```{r}
hardship_data_complete$hardship=(hardship_data_complete$mean_homicide+hardship_data_complete$gdp+hardship_data_complete$gini_income+hardship_data_complete$life_expect+hardship_data_complete$Infant_mortality+hardship_data_complete$primary_female_enrollment_rate)/6

hardship_data_complete
```

# Comparison of Intercept Values between GPS and WVS Data
```{r}
# Plotting comparing interecepts
ggplot(new_data, aes(x = intercept_gps, y = intercept_WVS, label = isocode)) +
  geom_point(size = 1.5) +
  geom_text(aes(label = isocode), vjust = -0.5, hjust = -0.5) +
  geom_smooth(method = "lm", se = FALSE, linetype = "dashed") +
  labs(title = "Comparison of Intercept Values",
       x = "Intercept_gps",
       y = "Intercept_WVS") +
  theme_minimal() +
  xlim(c(0, 1.2)) +
  ylim(c(0, 1.2)) +
  coord_fixed()

# Assuming you have a data frame named 'new_data' with columns 'intercept_gps', 'intercept_WVS', and 'isocode'

ggplot(new_data, aes(x = intercept_gps, y = intercept_WVS, label = isocode)) +
  geom_point(size = 3) +
  geom_text_repel(
    aes(label = isocode),
    box.padding = 0.5,
    point.padding = 0.1,
    force = 5
  ) +
  geom_smooth(method = "lm", se = FALSE, linetype = "dashed") +
  labs(x = "Intercept Global Preference Study",
       y = "Intercept World Value Survey") +
  theme_minimal() +
  xlim(c(0, 1.07)) +
  ylim(c(0, 1.07)) +
  coord_fixed()

# Annotate with word cloud
wordcloud(words = new_data$isocode, freq = rep(1, nrow(new_data)), scale = c(2, 0.5))

# Annotate with word cloud
wordcloud(words = new_data$isocode, freq = rep(1, nrow(new_data)), scale = c(2, 0.5))

# Assuming merged_results has columns intercept_gps and intercept_WVS
model <- lm(intercept_WVS ~ intercept_gps, data = merged_results)

# View the summary of the regression model
summary(model)

# Calculate the correlation
correlation <- cor(merged_results$intercept_gps, merged_results$intercept_WVS)

# Print the correlation coefficient
print(correlation)
```

#Comparison of the Effect of Age on Risk Taking between GPS and WVS Data
```{r}
# Plotting using ggplot2
ggplot(new_data, aes(x = slope_age_gps, y = slope_age_WVS, label = isocode)) +
  geom_point(size = 3) +
  geom_text_repel(
    aes(label = isocode),
    box.padding = 0.5,
    point.padding = 0.1,
    force = 5
  ) +
  geom_smooth(method = "lm", se = FALSE, linetype = "dashed") +
  labs(x = "Effect of Age on Risk Taking Global Preference Study",
       y = "Effect of Age on Risk Taking World Value Survey") +
  theme_minimal() +
  xlim(-0.5, 0) +
  ylim(c(-0.5, 0)) +
  coord_fixed()

new_data

correlation <- cor(new_data$slope_age_gps, new_data$slope_age_WVS)

# Print the correlation coefficient
print(correlation)
```


#Comparison of the Effect of Gender on Risk Taking between GPS and WVS Data
```{r}
# Plotting using ggplot2
ggplot(new_data, aes(x = slope_gender_gps, y = slope_gender_WVS, label = isocode)) +
  geom_point(size = 3) +
  geom_text_repel(
    aes(label = isocode),
    box.padding = 0.5,
    point.padding = 0.1,
    force = 5
  ) +
  geom_smooth(method = "lm", se = FALSE, linetype = "dashed") +
  labs(x = "Effect of Gender on Risk Taking Global Preference Study",
       y = "Effect of Gender on Risk Taking World Value Survey") +
  theme_minimal() +
  xlim(-0.6, 0.12) +
  ylim(c(-0.6, 0.12)) +
  coord_fixed()

new_data

correlation <- cor(new_data$slope_gender_gps, new_data$slope_gender_WVS)

# Print the correlation coefficient
print(correlation)
```

#Calculation of Hardship Index for WVS Data
```{r}
#hardship for WVS
hardship_values <- read_excel("/Users/laurabazzigher/Documents/GitHub/risk_wvs/data/dataset/Hardship/hardship_complete_2024.xlsx") 

labels <- c("country", "mean_homicide", "gdp", "gini_income", "Infant_mortality", "life_expect", "isocode", "primary_female_enrollment_rate")

print(hardship_values)

# Replace the column names as per your actual column names
# Z-standardize specific columns
hardship_values$gdp <- scale(hardship_values$gdp)
hardship_values$gini_income <- scale(hardship_values$gini_income)
hardship_values$Infant_mortality <- scale(hardship_values$Infant_mortality)
hardship_values$life_expect <- scale(hardship_values$life_expect)
hardship_values$mean_homicide <- scale(hardship_values$mean_homicide)
hardship_values$primary_female_enrollment_rate <- scale(hardship_values$primary_female_enrollment_rate)

hardship_values

hardship_values <- hardship_values%>%
  mutate(hardship = (mean_homicide + gdp + Infant_mortality + life_expect + gini_income + primary_female_enrollment_rate) / 6)
hardship_values
hardship_data_complete <- left_join(regression_results_WVS, hardship_values, by = "country")
hardship_data_complete
```

#Relationship between Hardship and Risk Taking for WVS Data
```{r}
#For WVS
ggplot(hardship_data_complete, aes(x = hardship, y = intercept, label = isocode)) +
  geom_point(size = 3) +
  geom_text_repel(
    aes(label = isocode),
    box.padding = 0.5,
    point.padding = 0.1,
    force = 5
  ) +
  geom_smooth(method = "lm", se = FALSE, linetype = "dashed") +
  labs(x = "Hardship",
       y = "Risk Taking") +
  theme_minimal() +
  xlim(-2, 2) +
  ylim(-0.6, 1) +
  coord_fixed(ratio = 2.5)
```

# Association between Hardship and Age Effect on Risk Taking for WVS Data
```{r}
#For WVS
ggplot(hardship_data_complete, aes(x = hardship, y = slope_age, label = isocode)) +
  geom_point(size = 3) +
  geom_text_repel(
    aes(label = isocode),
    box.padding = 0.5,
    point.padding = 0.1,
    force = 5
  ) +
  geom_smooth(method = "lm", se = FALSE, linetype = "dashed") +
  labs(x = "Hardship",
       y = "Age Effect") +
  theme_minimal() +
   xlim(-2, 2) +
  coord_fixed(ratio = 8)
```

# Relationship between Hardship and Risk Taking with Regression Line
```{r}
ggplot(hardship_data_complete, aes(x = hardship, y = intercept, label = isocode)) +
  geom_point(size = 3) +
  geom_text_repel(
    aes(label = isocode),
    box.padding = 0.5,
    point.padding = 0.1,
    force = 5
  ) +
  geom_smooth(method = "lm", se = FALSE, linetype = "dashed") +
  labs(x = "Hardship",
       y = "Risk Taking") +
  theme_minimal() +
  coord_fixed()
```

# Linear Model Summary: Hardship and Risk Taking Relationship
```{r}
# Lineares Modell für den ersten Fall
model_intercept <- lm(hardship ~ intercept, data = hardship_data_complete)
summary_intercept <- summary(model_intercept)
print(summary_intercept)

# Correlation Hardship und Risk Taking
correlation <- cor(hardship_data_complete$hardship, hardship_data_complete$intercept)

print(paste("Correlation Hardship und Risk Taking:", correlation))
```

# Linear Model Summary: Relationship Between Hardship and Age Effect on Risk Taking
```{r}
# Lineares Modell für den ersten Fall
model_intercept <- lm(hardship ~ slope_age, data = hardship_data_complete)
summary_intercept <- summary(model_intercept)
print(summary_intercept)

# Correlation Hardship und Risk Taking
correlation <- cor(hardship_data_complete$hardship, hardship_data_complete$slope_age)

print(paste("Correlation Hardship und Risk Taking:", correlation))
```
# Linear Model Summary: Relationship Between Hardship and Gender Effect on Risk Taking
```{r}
# Lineares Modell für den ersten Fall
model_intercept <- lm(hardship ~ slope_gender, data = hardship_data_complete)
summary_intercept <- summary(model_intercept)
print(summary_intercept)

# Correlation Hardship und Risk Taking
correlation <- cor(hardship_data_complete$hardship, hardship_data_complete$slope_gender)

print(paste("Correlation Hardship und Risk Taking:", correlation))
```

# Analysis of Risk Taking vs. Age with Gender Factor in WVS Data
```{r}
WVS_data
# Lineares Modell für Risk Taking vs. Age
model_risk_age <- lm(Z_score_risktaking ~ z_score_age + factor(gender), data = WVS_data)
summary_risk_age <- summary(model_risk_age)
print(summary_risk_age)

correlation <- by(WVS_data, WVS_data$gender, function(x) cor(x$z_score_age, x$Z_score_risktaking))

print(paste("Correlation Hardship und Risk Taking:", correlation))
```

# show new_data
```{r}
new_data
```

# Comparison of Gender Effects on Risk Taking Between Global Preference Study and World Value Survey Data
```{r}
# Lineares Modell für Risk Taking vs. Age
model <- lm(slope_gender_gps ~ slope_gender_WVS, data = new_data)
summary_model <- summary(model)
print(summary_model)

correlation <- cor(new_data$slope_age_gps, new_data$slope_age_WVS)
print(paste("Correlation Hardship und Risk Taking:", correlation))
```

# Relationship between Hardship and Gender Effect on Risk Taking
```{r}
ggplot(hardship_data_complete, aes(x = hardship, y = slope_gender, label = isocode)) +
  geom_point(size = 3) +
  geom_text_repel(
    aes(label = isocode),
    box.padding = 0.5,
    point.padding = 0.1,
    force = 5
  ) +
  geom_smooth(method = "lm", se = FALSE, linetype = "dashed") +
  labs(x = "Hardship",
       y = "Gender Effect") +
  theme_minimal() +
   xlim(-2, 2) +
  coord_fixed(ratio = 6)
```



